### 2025-05-12 AIAA2290/report/main.tex
Initialize the AIAA2290 report

% CVPR 2025 Paper Template; see https://github.com/cvpr-org/author-kit

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage{cvpr}              % To produce the CAMERA-READY version
% \usepackage[review]{cvpr}      % To produce the REVIEW version
% \usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Import additional packages in the preamble file, before hyperref
\input{preamble}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, 
% e.g. with the file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete *.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you should be clear).
\definecolor{cvprblue}{rgb}{0.21,0.49,0.74}
\usepackage[pagebackref,breaklinks,colorlinks,allcolors=cvprblue]{hyperref}

\usepackage{algorithm,algpseudocode,float}
\usepackage{lipsum}

\makeatletter
\newenvironment{breakablealgorithm}
  {% \begin{breakablealgorithm}
   \begin{center}
     \refstepcounter{algorithm}% New algorithm
     \hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
     \renewcommand{\caption}[2][\relax]{% Make a new \caption
       {\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}%
       \ifx\relax##1\relax % #1 is \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
       \else % #1 is not \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
       \fi
       \kern2pt\hrule\kern2pt
     }
  }{% \end{breakablealgorithm}
     \kern2pt\hrule\relax% \@fs@post for \@fs@ruled
   \end{center}
  }
\makeatother

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\paperID{*****} % *** Enter the Paper ID here
\def\confName{CVPR}
\def\confYear{2025}

\title{Exploration of Adversarial Training}

%%%%%%%%% AUTHORS - PLEASE UPDATE
\author{Jiarui HE\\
50013538 \\
{\tt\small jhe218@connect.hkust-gz.edu.cn}
}

\begin{document}
\maketitle

\section{Introduction}

This paper first introduces adversarial training and other methods for defence again adversarial training. 
Then some evaluation and comparation of mentioned methods. The final part is the

\section{Methods}
Let $\theta$ be the parameters of models, $f_\theta(\cdot)$ be the model, $\epsilon$ be the range of perturb of attack sample and $L$ be the loss function.

Then the target of adversarial training can be

$$
\theta^*=\arg\min_\theta\left\{
    \mathbb{E}_{(\mathbf{x}, \mathbf{y})\in \mathcal{D}}
    \left[
        \max_{\lVert\mathbf{\delta}\rVert\leq \epsilon}
            \left\{L(f_\theta(\mathbf{x}+\delta), y)\right\}
    \right]
\right\}
$$

There are some wide used algorithms for adversarial training.
For example, one of the most classical algorithms is the projected gradient descents (PGD).
Additionally, there are some algorithms which are base on this algorithms and make some modifies on it.
Furthermore, some structure applies adversarial training, such as GAN.

\subsection{Projected Gradient Descent}

This method try to construct attack samples using iteration towards the direction that relates to the gradient of loss function w.r.t. the input, 
which is usually the normalized value of $\nabla_{\mathbf{x}}(L(f_\theta(\mathrm{x}+\delta), y))$. People tend to use $l_0, l_2$ and $l_{\infty}$. Addtionally, the magnitude of iteration step is defined by a hyperparameter $\alpha$ .

The pesuado code of this algorithm is shown below:

\begin{breakablealgorithm}
\caption{PGD training}
\begin{algorithmic}[1] %每行显示行号
    \Require training set $\mathcal{D}$, learning rate $\tau$, training epochs $N$, hyperparameters $\alpha, \epsilon$, model $f_\theta$ and loss function $L$
    \State Initialize model parameters $\theta$

    \While 
    \EndWhile
\end{algorithmic}
\end{breakablealgorithm}

\end{document}

### 2025-05-12 UCUG1505/Proj/VisualVersion/detect_face.py
Update UCUG1505 Project

@@ -15,7 +15,8 @@ def detect() -> tuple[int, int] | None :
     gray = cv2.cvtColor(frame, cv2.COLOR_BGR2GRAY)
 
     # 检测正脸
-    faces = frontal_cascade.detectMultiScale(gray, scaleFactor=1.1, minNeighbors=5, minSize=(30,30))
+    # faces = []
+    faces = frontal_cascade.detectMultiScale(gray, scaleFactor=1.1, minNeighbors=8, minSize=(30,30))
     # 检测侧脸（左右侧皆可）
     profiles = profile_cascade.detectMultiScale(gray, scaleFactor=1.1, minNeighbors=5, minSize=(30,30))
 
@@ -27,10 +28,12 @@ def detect() -> tuple[int, int] | None :
     # 绘制框
     for (x, y, w, h) in detections:
         # cv2.rectangle(frame, (x, y), (x + w, y + h), (0,255,0), 2)
-        if (w < 80 or h < 80) : continue
+        if (w < 90 or h < 80) : continue
         if lrgSz < w * h :
             lrgSz = w * h
             res = (x + w / 2, y + h / 2)
+
+    
 
     # cv2.imshow('Head Detection', frame)
     res = (res[0] / frame.shape[1], res[1] / frame.shape[0]) if res else None

### 2025-05-12 UCUG1505/Proj/VisualVersion/ui.py

@@ -5,67 +5,114 @@ import numpy as np
 import pygame as pyg
 import lib
 
-screenWidth = 360
-screenHeight = 640
+screenWidth = 400
+screenHeight = 800
 
 PlayerRadius = 30
-BallRadius = 20
-DefenderRadius = 25
+BallRadius = 10
+DefenderRadius = 15
 
 PlayerMass = 30
 BallMass = 10
 DefenderMass = 25
 
-GateHeight = BallRadius
+BorderWidth = 25
 
-DefenderPosY = GateHeight + 10 + DefenderRadius
+GateRadius = 70
+
+BallInitPos = np.array([screenWidth / 2, screenHeight * 2 / 3])
+PlayerInitPos = np.array([screenWidth / 2, screenHeight * 3 / 4])
+GatePos = np.array([screenWidth / 2, 10])
+
+DefenderPosY = GateRadius + 10 + DefenderRadius
 
 radius = [PlayerRadius, BallRadius, DefenderRadius]
 mass = [PlayerMass, BallMass, DefenderMass]
 
 def calcPlayerPos(curPlayerPos : np.ndarray, nxtPlayerPos : np.ndarray) :
 	dis : np.ndarray = np.sqrt(((nxtPlayerPos - curPlayerPos) ** 2).sum()) + 1
-	return (curPlayerPos + (nxtPlayerPos - curPlayerPos) * min(max(0.1, math.log(dis.item()) / 5), 0.5))
+	vel = (nxtPlayerPos - curPlayerPos) * min(max(0.1, math.log(dis.item()) / 5), 0.5)
+	return (curPlayerPos + vel)
 
 def calcPlayerVelocity(curPlayerPos : np.ndarray, nxtPlayerPos : np.ndarray, deltaTime : float) -> np.ndarray :
 	return (nxtPlayerPos - curPlayerPos) / deltaTime
 
 def checkInDefendRange(curBallPos : np.ndarray) -> bool :
-	if curBallPos[1] < screenHeight / 3 : 
+	if curBallPos[1] < screenHeight / 2 : 
 		return True
 	return False
 
-def calcDefenderTarget(curPlayerPos : np.ndarray, curBallPos : np.ndarray, curBallVel : np.ndarray) -> np.ndarray :
-	intersect1 = lib.intersection(np.array([0, DefenderPosY]), np.array([screenWidth, DefenderPosY]), curBallPos, curBallPos + curBallVel)
[…]

### 2025-05-13 AIAA2290/report/main.tex
Update AIAA2290 report

@@
 
-\subsection{Projected Gradient Descent}
+\subsection{Projected Gradient Descent (PGD)}
 
@@
 People tend to use $l_0, l_2$ and $l_{\infty}$.
-Addtionally, the magnitude of iteration step is defined by a hyperparameter $\alpha$ .
+Addtionally, the magnitude of iteration step is defined by a hyperparameter $\alpha$ , while the number of step for each generation of attack sample is defined by another hyperparameter $k$ .
+
+For a PGD process with specific number of iteration $k$, we can call it $k$-PGD.
 
@@
 
-    \While 
-    \EndWhile
+  \For {$n=1$ to $N$}
+    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \mathbf{y})\}$}
+    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}}$ 
+      \State {$\delta\leftarrow$ zero matrix with shape of $X$}
+      \For {$t\leftarrow 1$ to $k$}
+        \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_{\theta}(\mathrm{X}+\delta), y))$
+        \State $\delta\leftarrow \mathrm{clamp}(\delta + \alpha g_a, -\epsilon, \epsilon)$
+      \EndFor
+      \State $g_\theta\leftarrow \nabla_{\theta}(L(f_{\theta}(\mathrm{X}+\delta), y))$
+      \State $\theta \leftarrow \theta - \tau g_\theta$
+    \EndFor
+  \EndFor
 \end{algorithmic}
@@
 
+Overall, the times of forward propagation and backpropagation of this algorithm are both $\Theta (NMk)$, where $M$ is the number of mini-batches
+
+\subsection{You can Only Propagate Once (YOPO)}
+
+To increase the efficience of adversarial training,
+
 \end{document}

### 2025-05-14 DSAA2011/Proj/cluster.py
Add prediction part to Proj of DSAA2011

@@ -25,8 +25,9 @@ if __name__ == "__main__" :
 
 	x_dem = visualize.dimension_reduction(X, 2, "TSNE")
 
-	labels_km, centers_km = kmeans(x_dem, 24, 20)
-	labels_hc, centers_hc = hierarchical(x_dem, 24)
+	labels_dem, centers_dem = kmeans(x_dem, 6, 20)
+	# cluster using the orginal data
+	labels_org, children_org = kmeans(X, 6, 20)
 	# create two figures at the same time
-	visualize.plot([x_dem, x_dem, x_dem], [labels_hc, labels_km, y], 2, need_dimension_reduction=False)
+	visualize.plot([x_dem, x_dem, x_dem], [labels_dem, labels_org, y], 2, need_dimension_reduction=False)
 	

### 2025-05-14 DSAA2011/Proj/predict.py

@@ -1,0 +1,27 @@
+import data
+from sklearn.linear_model import LogisticRegression
+from sklearn.preprocessing import StandardScaler
+from sklearn.metrics import accuracy_score, classification_report
+
+if __name__ == "__main__":
+	# Load the data
+	X_train, y_train = data.load_data("./Data/train", "train")
+
+	X_test, y_test = data.load_data("./Data/test", "test")
+
+	lr = LogisticRegression(C=1e9, max_iter=1000)
+
+	scaler = StandardScaler()
+	# X_train = scaler.fit_transform(X_train)
+	# X_test = scaler.transform(X_test)
+
+	lr.fit(X_train, y_train)
+
+	y_pred = lr.predict(X_test)
+
+	print("Accuracy:", accuracy_score(y_test, y_pred))
+	print(classification_report(y_test, y_pred))
+
+	
+
+	

### 2025-05-15 DSAA2011/Proj/predict.py
Add note of bagging into DSAA2011

@@ -1,7 +1,44 @@
 import data
 from sklearn.linear_model import LogisticRegression
+from sklearn.tree import DecisionTreeClassifier
+from sklearn.ensemble import RandomForestClassifier
+
 from sklearn.preprocessing import StandardScaler
 from sklearn.metrics import accuracy_score, classification_report
+
+def pred_lr(X_train, y_train, X_test, y_test):
+	# Logistic Regression
+	lr = LogisticRegression(C=1e9, max_iter=1000)
+	lr.fit(X_train, y_train)
+	y_pred = lr.predict(X_test)
+	print("Logistic Regression Accuracy:", accuracy_score(y_test, y_pred))
+	print(classification_report(y_test, y_pred))
+
+def pred_dt(X_train, y_train, X_test, y_test):
+
+	scaler = StandardScaler()
+	X_train = scaler.fit_transform(X_train.data)
+	X_test = scaler.transform(X_test.data)
+
+
+	dt = DecisionTreeClassifier()
+	dt.fit(X_train, y_train)
+	y_pred = dt.predict(X_test)
+	print("Decision Tree Accuracy:", accuracy_score(y_test, y_pred))
+	print(classification_report(y_test, y_pred))
+
+def pred_rf(X_train, y_train, X_test, y_test):
+
+	scaler = StandardScaler()
+	X_train = scaler.fit_transform(X_train.data)
+	X_test = scaler.transform(X_test.data)
+
+	# Random Forest
+	rf = RandomForestClassifier(n_estimators=100)
+	rf.fit(X_train, y_train)
+	y_pred = rf.predict(X_test)
+	print("Random Forest Accuracy:", accuracy_score(y_test, y_pred))
+	print(classification_report(y_test, y_pred))
 
 if __name__ == "__main__":
 	# Load the data
@@ -9,19 +46,9 @@ if __name__ == "__main__":
 
 	X_test, y_test = data.load_data("./Data/test", "test")
 
-	lr = LogisticRegression(C=1e9, max_iter=1000)
-
-	scaler = StandardScaler()
-	# X_train = scaler.fit_transform(X_train)
-	# X_test = scaler.transform(X_test)
-
-	lr.fit(X_train, y_train)
-
-	y_pred = lr.predict(X_test)
-
-	print("Accuracy:", accuracy_score(y_test, y_pred))
-	print(classification_report(y_test, y_pred))
-
+	# Standardize the data
 	
-
-	
[…]

### 2025-05-22 AIAA2290/report/rebuttal.tex
Update report of AIAA2290

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage[rebuttal]{cvpr}

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% Import additional packages in the preamble file, before hyperref
\input{preamble}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\definecolor{cvprblue}{rgb}{0.21,0.49,0.74}
\usepackage[pagebackref,breaklinks,colorlinks,allcolors=cvprblue]{hyperref}

% If you wish to avoid re-using figure, table, and equation numbers from
% the main paper, please uncomment the following and change the numbers
% appropriately.
%\setcounter{figure}{2}
%\setcounter{table}{1}
%\setcounter{equation}{2}

% If you wish to avoid re-using reference numbers from the main paper,
% please uncomment the following and change the counter value to the
% number of references you have in the main paper (here, 100).
%\makeatletter
%\apptocmd{\thebibliography}{\global\c@NAT@ctr 100\relax}{}{}
%\makeatother

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\paperID{*****} % *** Enter the Paper ID here
\def\confName{CVPR}
\def\confYear{2023}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.
Please follow the steps and style guidelines outlined below for submitting your author response.

The author rebuttal is optional and, following similar guidelines to previous conferences, is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers.
It is NOT intended to add new contributions (theorems, algorithms, experiments) that were absent in the original submission and NOT specifically requested by the reviewers.
You may optionally add a figure, graph, or proof to your rebuttal to better illustrate your answer to the reviewers' comments.

Per a passed 2018 PAMI-TC motion, reviewers should refrain from requesting significant additional experiments for the rebuttal or penalize for lack of additional experiments.
Authors should refrain from including new experimental results in the rebuttal, especially when not specifically requested to do so by the reviewers.
Authors may include figures with illustrations or comparison tables of results reported in the submission/supplemental material or in other papers.

Just like the original submission, the rebuttal must maintain anonymity and cannot include external links that reveal the author identity or circumvent the length restriction.
The rebuttal must comply with this template (the use of sections is not required, though it is recommended to structure the rebuttal for ease of reading).

%-------------------------------------------------------------------------

\subsection{Response length}
Author responses must be no longer than 1 page in length including any references and figures.
Overlength responses will simply not be reviewed.
This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The top margin should begin 1 inch (2.54 cm) from the top edge of the page.
The bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the page.

Please number any displayed equations.
It is important for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.
Main text should be in 10-point Times, single-spaced.
Section headings should be in 10 or 12 point Times.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Figure and table captions should be 9-point Roman type as in \cref{fig:onecol}.

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response.
When referenced in the text, enclose the citation number in square brackets, for example~\cite{zhang2019propagateonceacceleratingadversarial}.
Where appropriate, include the name(s) of editors of referenced books.

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{0.5in} \rule{0.9\linewidth}{0pt}}
  %\includegraphics[width=0.8\linewidth]{egfigure.eps}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
   \label{fig:onecol}
\end{figure}

To avoid ambiguities, it is best if the numbering for equations, figures, tables, and references in the author response does not overlap with that in the main paper (the reviewer may wonder if you talk about \cref{fig:onecol} in the author response or in the paper).
See \LaTeX\ template for a workaround.

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
Please ensure that any point you wish to make is resolvable in a printed copy of the response.
Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your response in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it is almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%%%%%%%%% REFERENCES
{
    \small
    \bibliographystyle{ieeenat_fullname}
    \bibliography{references}
}

\end{document}

### 2025-05-22 AIAA2290/report/main.tex
Update report of AIAA2290

@@
 
+\begin{abstract}
+
+\end{abstract}
+
 \section{Introduction}
 
-This paper first introduces adversarial training and other methods for defence again adversarial training. 
-Then some evaluation and comparation of mentioned methods. The final part is the
+Adversarial training is an essential part of artificial intelligence application, especially the application of nerual network.
+It may increase the robustness of models and help defend against perturbed input, especially those designed specifically to attack the model.
+Adversarial training can enhance the security and reliability of artificial intelligence.
+Furthermore, related concepts also contribute to the development of generative artificial intelligence.
 
-\section{Methods}
+Section 2 shows some widely used training algorithms.
+And Section 3 demonstrates the result of an instance of adversarial traning and its result.
+Section 4 aims to discuss the issues of adversarial training.
+Section 5 presents further application of adversarial traning.
+
+\section{Training Algorithms}
 Let $\theta$ be the parameters of models, $f_\theta(\cdot)$ be the model, $\epsilon$ be the range of perturb of attack sample and $L$ be the loss function.
@@
 
-$$
+\begin{equation}
 \theta^*=\arg\min_\theta\left\{
@@
 \right\}
-$$
+\tag{2:1}
+\label{formula:adversarial_target}
+\end{equation}
 
@@
 
-For a PGD process with specific number of iteration $k$, we can call it $k$-PGD.
+For a PGD process with specific number of iteration $k$, we can call it PGD-$k$.
 
@@
 \begin{algorithmic}[1] %每行显示行号
-  \Require training set $\mathcal{D}$, learning rate $\tau$, training epochs $N$, hyperparameters $\alpha, \epsilon$, model $f_\theta$ and loss function $L$
+  \Require training set $\mathcal{D}$, learning rate $\tau$, training epochs $N$, hyperparameters $\alpha, \epsilon, k$, model $f_\theta$ and loss function $L$
   \State Initialize model parameters $\theta$
@@
     \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \mathbf{y})\}$}
-    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}}$ 
+    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}$} 
       \State {$\delta\leftarrow$ zero matrix with shape of $X$}
       \For {$t\leftarrow 1$ to $k$}
+        \State {execute backpropagation}
         \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_{\theta}(\mathrm{X}+\delta), y))$
-        \State $\delta\leftarrow \mathrm{clamp}(\delta + \alpha g_a, -\epsilon, \epsilon)$
+        \State $\delta\leftarrow \mathrm{clamp}(\delta + \frac{\alpha}{\left\lVert g_a \right\rVert}g_a, -\epsilon, \epsilon)$
       \EndFor
@@
 
-To increase the efficience of adversarial training,
+This training methods aims to enhance the efficiency of traning by reducing the frequency of entire backpropagation.
+According to the pontryagin maximum principle (PMP), this algorithm assumes that the model mainly use the first layer to handle the attack.
+Thus, the process of gradient calculation can reuse the gradients excepts the first layer.
 
+Training on one mini-batch is an $m\times n$ loop, where $m, n$ are both hyperparameters.
+In the outer loop, program will execute the entire backpropagation once and get the gradients of the layers excepts the first, then execute the inner loop to calculate the gradient of the first layer and iterate the attack sample.
+A YOPO process with specific $m, n$ is noted by YOPO-$m$-$n$ .
+
+The pesuado code of this algorirthm is shown below:
+
+\begin{breakablealgorithm}
+\caption{YOPO training}
+\begin{algorithmic}[1]
+  \Require training set $\mathcal{D}$, learning rate $\tau$, training epochs $N$, hyperparameters $\alpha, \epsilon, m, n$, model $f_\theta$ and loss function $L$ 
+  \State divide the model paramters $\theta$ into first layer $\theta_0$ and the other layers $\theta'$
+  \For {$i\leftarrow 1$ to $N$}
+    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \mathbf{y})\}$}
+    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}$}
+      \State $\delta_{0, n}\leftarrow \text{zero matrix with shape of } \mathrm{X}$
+      \State $g_\theta\leftarrow \text{zero matrix with shape of } \mathrm{\theta}$
+      \For {$j=1$ to $m$}
+        \State execute entire backpropagation
+        \State $\delta_{j,0}\leftarrow \delta_{j-1,n}$
+        \State {$p\leftarrow \nabla_{f_{\theta_0}(\mathrm{X}+\delta_{j,0})}\left(
+          L(f_\theta(\mathrm{X}+\delta_{j,0}), \mathbf{y})
+        \right)$}
+        \For {$k=1$ to $n$}
+          \State $g_a\leftarrow
+            p\cdot \nabla_{\mathrm{X}+\delta}(f_{\theta_0}(\mathrm{X}+\delta_{j,k-1}))$
+          \State $\delta_{j,k}\leftarrow \mathrm{clamp}\left(\delta_{j,k-1}+\frac{\alpha\cdot g_a}{\left\lVert g_a \right\rVert}, -\epsilon, \epsilon\right)$
+        \EndFor
+        \State $g_\theta\leftarrow g_\theta + \nabla_{\theta}(L(f_{\theta}(\mathrm{X}+\delta_{j,n}), \mathbf{y}))$
+        \Comment this gradient can be calculated in backpropagation
+      \EndFor
+      \State $\theta\leftarrow \theta-\tau\cdot g_\theta$
+    \EndFor
+  \EndFor
+\end{algorithmic}
+\end{breakablealgorithm}
+For one mini-batch, entire backpropagation is executed only for $\Theta(m)$ times, however, the number of iterations of attack sample is $\Theta(mn)$ .
+Additionally, according to the paper by Zhang D, el tal.
+\cite{zhang2019propagateonceacceleratingadversarial} .
+When $m\times n$ is slightly larger than $k$ , then YOPO-$m$-$n$ can achieve similar performance with PGD-$k$ .
+
+However, there are analysis \cite{zhu2020freelbenhancedadversarialtraining} which claims that the PMP-based assumption does not hold on ReLU-based models.
+
+\subsection{Free Large Batch Adversarial Attack (FreeLB)}
+
+Different from that PGD iterates the attack sample for $k$ times and only apply it to update the model with the final sample, FreeLB use average to use all the samples in iteration process.
+
+This algorithm can be treated as a case of YOPO when we set $n=1$ , but it can work on ReLU-bases models.
+
+Here is a comparison with PGD: The process of PGD is to find a attack sample by multiple maximization of the loss function, then minimize the loss once by gradient descent.
+FreeLB, however, minimizes the loss after each miximization operation.
+This modify can increase the robustness and increase the performance of training.
+
+The pesuado code of this algorirthm is shown below:
+
+\begin{breakablealgorithm}
+\caption{FreeLB training}
+\begin{algorithmic}[1]
+  \Require traning set $\mathcal{D}$, learning rate $\tau$, traning epochs $N$, hyperparameters $\alpha, \epsilon, k$, model $f_\theta$ and loss function $L$ .
+  \For {$i\leftarrow 1$ to $N$}
+    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \mathbf{y})\}$}
+    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}$}
+      \State $\delta_0\leftarrow \textbf{random}\text{ matrix with shape of } \mathrm{X}$
+      \State $g_\theta\leftarrow \text{zero matrix with shape of } \theta$
+      \For {$i\leftarrow 1$ to $k$}
+        \State {execute backpropagation}
+        \State $g_\theta\leftarrow g_\theta + \frac{1}{k}\nabla_{\theta}(L(f_\theta(\mathrm{X}+\delta_{i-1}), \mathbf{y}))$
+        \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_\theta(\mathrm{X}+\delta_{i-1}), \mathbf{y}))$
+        \State $\delta_i\leftarrow \mathrm{clamp}\left(\delta_{i-1}+\frac{\alpha}{\left\lVert g_a \right\rVert}g_a, -\epsilon, \epsilon\right)$
+      \EndFor
+      \State {$\theta\leftarrow\theta-\tau g_\theta$}
+    \EndFor
+  \EndFor
+\end{algorithmic}
+\end{breakablealgorithm}
+
+\subsection{SMoothness-inducing Adversarial Regularization (SMART)}
+
+This algorithm does not aim to achieve the target shown above (\cref{formula:adversarial_target}) , but treats the preturbation as regularization item.
+It attempts to guide the model to output the same prediction for adjacent samples.
+
+The target formula is shown below :
+
+\begin{equation}
+  \theta^*=\arg\min_\theta\{\mathcal{L}(\theta)+\lambda \mathcal{R}(\theta)\}
+  \tag{2:4:1}
+  \label{formula:adversarial_target2}
+\end{equation}
+where $\mathcal{L}(\theta)$ is the sum of loss of the original dataset, $\lambda$ is the hyperparameter that $\lambda>0$ and $\mathcal{R}(\theta)$ is the smoothness-inducing adversarial regularizer.
+
+$$
+\begin{aligned}
+  &\mathcal{L}(\theta)=\frac{1}{n}\sum_{(\mathbf{x}, \mathbf{y})\in\mathcal{D}} L(f_\theta(\mathbf{x}), \mathbf{y}) \\
+  &\mathcal{R}(\theta)=\frac{1}{n}\sum_{(\mathbf{x}, \mathbf{y})\in\mathcal{D}} \max_{\left\Vert \tilde{\mathbf{x}}-\mathbf{x}\right\Vert\leq \epsilon}\left\{l\left(f_\theta(\tilde{\mathbf{x}}), f_\theta(\mathbf{x})\right)\right\}
+\end{aligned}
+$$
+
+and $l(a, b)$ is the symmetric KL divergence :
+
+$$
+l(a, b)=\mathrm{KL}(a, b) + \mathrm{KL}(b, a)
+$$
+
+To solve \cref{formula:adversarial_target2} , Bregman proximal point optimization is applied,
+
+{\small
+\bibliographystyle{ieeenat_fullname}
+\bibliography{references}
+}
 \end{document}

### 2025-05-22 UCUG1505/Proj/VisualVersion/detect_face.py
Update UI

@@ -16,9 +16,9 @@ def detect() -> tuple[int, int] | None :
 
     # 检测正脸
     # faces = []
-    faces = frontal_cascade.detectMultiScale(gray, scaleFactor=1.1, minNeighbors=8, minSize=(30,30))
+    faces = frontal_cascade.detectMultiScale(gray, scaleFactor=1.2, minNeighbors=8, minSize=(30,30))
     # 检测侧脸（左右侧皆可）
-    profiles = profile_cascade.detectMultiScale(gray, scaleFactor=1.1, minNeighbors=5, minSize=(30,30))
+    profiles = profile_cascade.detectMultiScale(gray, scaleFactor=1.2, minNeighbors=5, minSize=(30,30))
 
     # 合并结果（示例：直接拼接，生产可加去重）
     lrgSz = 0

### 2025-05-22 UCUG1505/Proj/VisualVersion/ui.py

@@ -14,15 +14,19 @@ DefenderRadius = 15
 
 PlayerMass = 30
 BallMass = 10
-DefenderMass = 25
+DefenderMass = 30
 
 BorderWidth = 25
 
 GateRadius = 70
+Winner = 0
 
-BallInitPos = np.array([screenWidth / 2, screenHeight * 2 / 3])
+ScorePlayer, ScoreDefender = 0, 0
+
+BallInitPos = np.array([screenWidth / 2, screenHeight / 2])
 PlayerInitPos = np.array([screenWidth / 2, screenHeight * 3 / 4])
 GatePos = np.array([screenWidth / 2, 10])
+OwnGatePos = np.array([screenWidth / 2, screenHeight - 10])
 
 DefenderPosY = GateRadius + 10 + DefenderRadius
 
@@ -31,16 +35,11 @@ mass = [PlayerMass, BallMass, DefenderMass]
 
 def calcPlayerPos(curPlayerPos : np.ndarray, nxtPlayerPos : np.ndarray) :
 	dis : np.ndarray = np.sqrt(((nxtPlayerPos - curPlayerPos) ** 2).sum()) + 1
-	vel = (nxtPlayerPos - curPlayerPos) * min(max(0.1, math.log(dis.item()) / 5), 0.5)
+	vel = (nxtPlayerPos - curPlayerPos) * min(max(0.1, math.log(dis.item()) / 5), 0.4)
 	return (curPlayerPos + vel)
 
 def calcPlayerVelocity(curPlayerPos : np.ndarray, nxtPlayerPos : np.ndarray, deltaTime : float) -> np.ndarray :
 	return (nxtPlayerPos - curPlayerPos) / deltaTime
-
-def checkInDefendRange(curBallPos : np.ndarray) -> bool :
-	if curBallPos[1] < screenHeight / 2 : 
-		return True
-	return False
 
 def calcDefenderTarget(curBallPos : np.ndarray) -> np.ndarray :
 	vec = curBallPos - GatePos
@@ -49,13 +48,31 @@ def calcDefenderTarget(curBallPos : np.ndarray) -> np.ndarray :
 def calcDefenderPos(curDefenderPos : np.ndarray, nxtDefenderPos : np.ndarray) :
 	dis : np.ndarray = np.sqrt(((nxtDefenderPos - curDefenderPos) ** 2).sum()) + 1
[…]

### 2025-05-23 AIAA2290/report/main.tex
Update report of AIAA2290

@@
 It attempts to guide the model to output the same prediction for adjacent samples.
+And this algorithm is shown to be effective for fine-tuning of pre-trained natural language processing model.
 
@@
 $$
-l(a, b)=\mathrm{KL}(a, b) + \mathrm{KL}(b, a)
+\begin{aligned}
+l(f, g)&=\mathrm{KL}(f, g) + \mathrm{KL}(f, g) \\
+&=\sum_{x\in \mathcal{X}} f(x)\log\frac{f(x)}{g(x)} + g(x)\log\frac{g(x)}{f(x)} \\
+&=\sum_{x\in \mathcal{X}} (f(x) - g(x))\log\frac{f(x)}{g(x)}
+\end{aligned}
 $$
 
-To solve \cref{formula:adversarial_target2} , Bregman proximal point optimization is applied,
+To solve \cref{formula:adversarial_target2} , Bregman proximal point optimization is applied, the key function of this algorithm is called Bregman divergence:
+
+$$
+\mathrm{Breg}_\mathcal{D}(\theta_1, \theta_2)=\frac{1}{\left\vert\mathcal{D}\right\vert}
+  \sum_{(\mathbf{x}, \mathbf{y})\in\mathcal{D}}l\left(f_{\theta_1}(\mathbf{x}), f_{\theta_2}(\mathbf{x})\right)
+$$
+
+Then for each mini-batch, algorithm applied this function as the loss function to iterate the attack sample.
+For more precisely, the formula of gradient of attack sample perturbation $\delta$ on dataset $\mathcal{D}$ is defined as :
+
+$$
+g_\theta(\mathcal{D}, \delta)=
+\begin{bmatrix}
+  \nabla_{\delta_1}l(f_\theta(\mathbf{x}_1), f_\theta(\mathbf{x}_1+\delta_1)) \\
+  \nabla_{\delta_2}l(f_\theta(\mathbf{x}_2), f_\theta(\mathbf{x}_2+\delta_2)) \\
+  \vdots \\
+  \nabla_{\delta_{|\mathcal{D}|}}l(f_\theta(\mathbf{x}_{|\mathcal{D}|}), f_\theta(\mathbf{x}_{|\mathcal{D}|}+\delta_{|\mathcal{D}|}))
+\end{bmatrix}
+$$
+
+Furthermore, this algorihtm applies momentum and Adam update rule for optimizing. Here is the pesuado code:
+
+\begin{breakablealgorithm}
+\caption{SMART algorirthm}
+\begin{algorithmic}[1]
+  \Require number of iteration of attack sample $k$, dataset $\mathcal{D}$, parameters of pre-trained model $\theta_0$ , number of epochs $N$, learning rate $\tau$, hyperparameters for iteration of attack sample $\alpha, \epsilon$, momentum parameter $\beta$
+
+  \State $\tilde{\theta_1}\leftarrow\theta_0$ 
+  \For {$t\leftarrow 1$ to $N$}
+    \State $\overline{\theta}\leftarrow \theta_{t-1}$
+    \State {divide $\mathcal{D}$ into mini-batches $\mathcal{C}$}
+    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}$}
+      \State initialize $\delta$ with guassian distribution
+      \State $\forall \delta _i\sim N(0,\sigma^2I)$
+      \For {$i=1$ to $k$}
+        \State $g_i\leftarrow \frac{g_{\overline{\theta}}\left((\mathrm{X},\mathbf{y}), \delta\right)}{\left\Vert g_{\overline{\theta}}((\mathrm{X},\mathbf{y}), \delta) \right\Vert}$
+        \State $\delta\leftarrow \mathrm{clamp}(\delta + \alpha g_i, -\epsilon, \epsilon)$
+      \EndFor
+      \State $\overline{\theta}\leftarrow \mathrm{Adam}\left(\overline{\theta}, (\mathrm{X}+\delta, \mathbf{y})\right)$
+    \EndFor
+    \State $\theta_t\leftarrow \overline{\theta}$
+    \State $\tilde{\theta}_{t+1}\leftarrow (1-\beta)\overline{\theta}+\beta\tilde{\theta}_t$
+  \EndFor
+  \State the output is $\theta_N$
+\end{algorithmic}
+\end{breakablealgorithm}
 

### 2025-05-24 AIAA2290/report/main.tex
Update AIAA 2290 report

@@
 \usepackage{lipsum}
+\usepackage{longtable}
+\usepackage{multirow}
 
@@
 \begin{abstract}
-
+This report examines the inherent challenges and limitations of adversarial training for neural networks.
+We highlight issues related to generalization, computational complexity, and performance trade-offs, and discuss potential directions for future research.
 \end{abstract}
@@
 
-Adversarial training is an essential part of artificial intelligence application, especially the application of nerual network.
-It may increase the robustness of models and help defend against perturbed input, especially those designed specifically to attack the model.
-Adversarial training can enhance the security and reliability of artificial intelligence.
-Furthermore, related concepts also contribute to the development of generative artificial intelligence.
+Adversarial training plays a fundamental role in artificial intelligence applications, particularly in the context of neural networks.
+By incorporating adversarial examples into the training process, models can achieve enhanced robustness against perturbed inputs, including those specifically crafted to deceive the network.
+Consequently, adversarial training bolsters the security and reliability of AI systems.
+Moreover, related methodologies have catalyzed significant advancements in generative artificial intelligence.
 
-Section 2 shows some widely used training algorithms.
-And Section 3 demonstrates the result of an instance of adversarial traning and its result.
-Section 4 aims to discuss the issues of adversarial training.
-Section 5 presents further application of adversarial traning.
+Section 2 reviews several widely adopted adversarial training algorithms.
+Section 3 presents a case study illustrating the impact of adversarial training on model performance.
+Section 4 examines the challenges and limitations inherent to adversarial training.
+Finally, Section 5 explores additional applications and future directions for this paradigm.
 
@@
 
-There are some wide used algorithms for adversarial training.
-For example, one of the most classical algorithms is the projected gradient descents (PGD).
-Additionally, there are some algorithms which are base on this algorithms and make some modifies on it.
-Furthermore, some structure applies adversarial training, such as GAN.
+Adversarial training plays a fundamental role in artificial intelligence applications, particularly in the context of neural networks.
+By incorporating adversarial examples into the training process, models can achieve enhanced robustness against perturbed inputs, including those specifically crafted to deceive the network.
+Consequently, adversarial training bolsters the security and reliability of AI systems.
+Moreover, related methodologies have catalyzed significant advancements in generative artificial intelligence.
+
+Section 2 and Section 3 reviews several widely adopted adversarial training algorithms.
+Section 4 presents a case study illustrating the impact of adversarial training on model performance.
+Section 5 examines the challenges and limitations inherent to adversarial training.
+Finally, Section 6 explores additional applications and future directions for this paradigm.
+
+\section{Adversarial Training Objective}
+Let $\theta$ denote the model parameters, $f_{\theta}(\cdot)$ the model mapping, $\epsilon$ the maximum allowable perturbation magnitude, and $L(\cdot,\cdot)$ the loss function.
+The objective of adversarial training can then be formulated as:
+
+\begin{equation}
+\theta^{*} = \arg\min_{\theta} ; \mathbb{E}{(\mathbf{x},\mathbf{y}) \sim \mathcal{D}} \Biggl[\underbrace{\max_{{\lVert \mathbf{\delta} \rVert \le \epsilon}} L\bigl(f_{\theta}(\mathbf{x} + \mathbf{\delta}), \mathbf{y}\bigr)}_{\text{worst-case loss}}\Biggr]
+\label{eq:adv_training_objective}
+\end{equation}
+
+Here, the inner maximization identifies the most adversarial perturbation $\mathbf{\delta}$ within the $\epsilon$-ball around the input $\mathbf{x}$, while the outer minimization optimizes the model parameters to minimize the expected worst-case loss over the data distribution $\mathcal{D}$.
+
+\section{Adversarial Training Algorithms}
+Several algorithms have been proposed to approximate the inner maximization in Equation~\eqref{eq:adv_training_objective}.
+Among these, the projected gradient descent (PGD) method is one of the most classical and widely used approaches.
+Subsequent techniques often build upon PGD, introducing modifications to improve efficiency, convergence, or transferability.
+Additionally, adversarial training has been integrated into generative frameworks such as Generative Adversarial Networks (GANs) to further enhance model robustness.
 
 \subsection{Projected Gradient Descent (PGD)}
+The PGD attack iteratively constructs adversarial examples by ascending the gradient of the loss with respect to the input.
+At each step, the perturbation is updated and then projected back onto the allowable perturbation set:
 
-This method try to construct attack samples using iteration towards the direction that relates to the gradient of loss function w.r.t. the input, 
-which is usually the normalized value of $\nabla_{\mathbf{x}}(L(f_\theta(\mathrm{x}+\delta), y))$.
-People tend to use $l_0, l_2$ and $l_{\infty}$.
-Addtionally, the magnitude of iteration step is defined by a hyperparameter $\alpha$ , while the number of step for each generation of attack sample is defined by another hyperparameter $k$ .
+$$
+\begin{aligned}
+\mathbf{\delta}_{0} &= \mathbf{0}, \\
+\mathbf{\delta}_{t+1} &= \Pi_{{\lVert \mathbf{\delta_t} \rVert \le \epsilon}} \Bigl(\mathbf{\delta}_{t} + \alpha \cdot \mathrm{sign}\bigl(\nabla_{\mathbf{x}} L(f_{\theta}(\mathbf{x} + \mathbf{\delta}_{t}), \mathbf{y})\bigr)\Bigr),
+\end{aligned}
+$$
 
-For a PGD process with specific number of iteration $k$, we can call it PGD-$k$.
+where:
 
-The pesuado code of this algorithm is shown below:
+$\alpha$ is the step size hyperparameter, and $k$ denotes the total number of iterations (denoted as PGD-$k$).
+
+$\Pi$ represents the projection operator onto the $\ell_{p}$-ball of radius $\epsilon$, commonly using $p=2$ or $p=\infty$.
+
+After $k$ iterations, the adversarial example is given by $\mathbf{x}^{\mathrm{adv}} = \mathbf{x} + \mathbf{\delta}_{k}$.
+Incorporating these examples into the training process yields the PGD adversarial training algorithm
 
@@
 
-This training methods aims to enhance the efficiency of traning by reducing the frequency of entire backpropagation.
+This training methods aims to enhance the efficiency of training by reducing the frequency of entire backpropagation.
 According to the pontryagin maximum principle (PMP), this algorithm assumes that the model mainly use the first layer to handle the attack.
@@
   \Require training set $\mathcal{D}$, learning rate $\tau$, training epochs $N$, hyperparameters $\alpha, \epsilon, m, n$, model $f_\theta$ and loss function $L$ 
-  \State divide the model paramters $\theta$ into first layer $\theta_0$ and the other layers $\theta'$
+  \State divide the model parameters $\theta$ into first layer $\theta_0$ and the other layers $\theta'$
   \For {$i\leftarrow 1$ to $N$}
@@
 For one mini-batch, entire backpropagation is executed only for $\Theta(m)$ times, however, the number of iterations of attack sample is $\Theta(mn)$ .
-Additionally, according to the paper by Zhang D, el tal.
+Additionally, according to the paper by Zhang D, et.
+al.
 \cite{zhang2019propagateonceacceleratingadversarial} .
@@
 FreeLB, however, minimizes the loss after each miximization operation.
-This modify can increase the robustness and increase the performance of training.
+This modify can increase the robustness and increase the performance of training \cite{zhu2020freelbenhancedadversarialtraining} .
 
@@
 \begin{algorithmic}[1]
-  \Require traning set $\mathcal{D}$, learning rate $\tau$, traning epochs $N$, hyperparameters $\alpha, \epsilon, k$, model $f_\theta$ and loss function $L$ .
+  \Require training set $\mathcal{D}$, learning rate $\tau$, training epochs $N$, hyperparameters $\alpha, \epsilon, k$, model $f_\theta$ and loss function $L$ .
   \For {$i\leftarrow 1$ to $N$}
@@
 
+However, conducting of entire backpropagation and gradient accumulation for each iteration may cause high time consumption. And this will be shown on \cref{table:instance_training-result}
+
 \subsection{SMoothness-inducing Adversarial Regularization (SMART)}
 
-This algorithm does not aim to achieve the target shown above (\cref{formula:adversarial_target}) , but treats the preturbation as regularization item.
+This algorithm does not aim to achieve the target shown above (\cref{eq:adv_training_objective}) , but treats the preturbation as regularization item.
 It attempts to guide the model to output the same prediction for adjacent samples.
-And this algorithm is shown to be effective for fine-tuning of pre-trained natural language processing model.
+And this algorithm is shown to be effective for fine-tuning of pre-trained natural language processing model \cite{Jiang_2020} .
 
@@
 \begin{aligned}
-l(f, g)&=\mathrm{KL}(f, g) + \mathrm{KL}(f, g) \\
+l(f, g)&=\mathrm{KL}(f\Vert g) + \mathrm{KL}(f\Vert g) \\
 &=\sum_{x\in \mathcal{X}} f(x)\log\frac{f(x)}{g(x)} + g(x)\log\frac{g(x)}{f(x)} \\
@@
   \vdots \\
-  \nabla_{\delta_{|\mathcal{D}|}}l(f_\theta(\mathbf{x}_{|\mathcal{D}|}), f_\theta(\mathbf{x}_{|\mathcal{D}|}+\delta_{|\mathcal{D}|}))
+  \nabla_{\delta_{|\mathcal{D}|}}l\left(f_\theta\left(\mathbf{x}_{|\mathcal{D}|}\right), f_\theta\left(\mathbf{x}_{|\mathcal{D}|}+\delta_{|\mathcal{D}|}\right)\right)
 \end{bmatrix}
@@
 \begin{breakablealgorithm}
-\caption{SMART algorirthm}
+\caption{SMART training}
 \begin{algorithmic}[1]
@@
 
+\section{An Instance of Adversarial Training}
+
+An instance of adversarial training is provided for better understanding of its features and evaluation, which includes the implementation of PGD and FreeLB.
+
+We applied \texttt{torch} library for training and testing, while dataset is MNIST, which is a typical dataset for image recognition.
+And the GPU and CPU are RTX2080Ti-22G and Intel-13900K respectively.
+
+For hyperparameter setting, the learing rate are all $1\times 10^{-4}$ and the training epochs are all $50$. Rule of gradient updating is Adam.
+
+The model is a simple convolution nerual network, whose architecture is shown below:
+
+\begin{table}[H]
+  \centering
+  \caption{Architecture of Model}
+  \label{table:instance_model-arch}
+  \begin{tabular}{cl}
+    \textbf{Structure} & \textbf{Parameters} \\
+    \hline
+    \multirow{4}*{Conv2d} & $\texttt{filter}=32$ \\
+    ~ & $\texttt{kernel}=5$ \\
+    ~ & $\texttt{padding}=2$ \\
+    ~ & $\texttt{bias}=\texttt{True}$ \\
+    \hline
+    \multirow{2}*{MaxPool2d} & $\texttt{kernel}=2$ \\
+    ~ & $\texttt{stride}=2$ \\
+    \hline
+    \multirow{4}*{Conv2d} & $\texttt{filter}=32$ \\
+    ~ & $\texttt{kernel}=5$ \\
+    ~ & $\texttt{padding}=2$ \\
+    ~ & $\texttt{bias}=\texttt{True}$ \\
+    \hline
+    \multirow{2}*{MaxPool2d} & $\texttt{kernel}=2$ \\
+    ~ & $\texttt{stride}=2$ \\
+    \hline
+    \multirow{2}*{Linear} & $\texttt{input}=7\times 7\times 64$ \\
+    ~ & $\texttt{output}=1024$ \\
+    \hline
+    \multirow{2}*{Linear} & $\texttt{input}=1024$ \\
+    ~ & $\texttt{output}=10$ \\
+  \end{tabular}
+\end{table}
+
+And here is the training result, where std represents the instance of training on original samples:
+
+\begin{table}[H]
+  \caption{Result of Adversarial Training}
+  \label{table:instance_training-result}
+  \begin{tabular}{lcccc}
+    \multirow{2}*{\textbf{Training}} & \multicolumn{3}{c}{\textbf{Testing}} & \multirow{2}*{\textbf{Time}(min)} \\
+    ~ & std & PGD-10 & PGD-40 & ~ \\
+    \hline
+    std & 98.46\% & 89.53\% & 56.40\% & 7.17 \\
+    PGD-10 & 97.36\% & 98.00\% & 90.03\% & 12.87  \\
+    PGD-40 & 88.36\% & 98.31\% & 95.81\% & 30.58 \\
+    FreeLB-10 & 98.34\% & 97.79\% & 87.50\% & 20.18 \\
+    FreeLB-40 & 94.96\% & 98.29\% & 94.90\% & 61.38 
+  \end{tabular}
+\end{table}
+
+The result shows some features and drawbacks of adversarial training.
+
+For one thing, the accuracy of recognition by models after adversarial training on original sample is lower than that trained with original dataset.
+Furthermore, the increase of number of iteration for generation of training attack sample, which corresponds to the increase of perturbation intensity, leads to the worse performance on original dataset.
+
+For another thing, the increase time consumption for adversarial training is also be considered in practical application.
+
+\section{Issues of Adversarial Training}
+Although Adversarial Training (AT) is widely regarded as an effective approach to enhancing the robustness of neural networks, numerous studies have highlighted its significant limitations across various aspects.
+
+\subsection{Generalization and Blind-Spot Attacks}
+Zhang et al.~\cite{zhang2019limitationsadversarialtrainingblindspot} pointed out that AT shows considerably weaker robustness against samples located in low-density regions of the training data distribution.
+These so-called "blind-spot samples" lie far from the main data manifold and are often underrepresented during training, making them vulnerable to blind-spot attacks.
+This problem is particularly pronounced in high-dimensional datasets such as CIFAR-10 and ImageNet.
+
+\subsection{Reliability Issues in Robot Learning}
+Lechner et al.~\cite{lechner2021adversarialtrainingreadyrobot} demonstrated that AT can introduce new risks in robotic learning systems, including transient errors, systemic biases, and conditional failures.
+These issues suggest that in dynamic and complex environments, AT may compromise the model’s stability and interpretability.
+
+\subsection{High Computational Cost}
+AT typically involves generating adversarial perturbations for each training example, such as using Projected Gradient Descent (PGD), which significantly increases training time and resource consumption.
+Zhao et al.~\cite{zhao2022review} noted that such overhead may become a bottleneck in real-world industrial deployments, especially in resource-constrained or latency-critical systems.
+
+\subsection{Accuracy Degradation on Clean Samples}
+Adversarial training often comes at the cost of reduced accuracy on clean (non-adversarial) inputs.
+Zhao et al.~\cite{a15080283} observed in their systematic review that this "robustness–accuracy trade-off" is a central challenge in current AT methods, and can be particularly problematic in domains where high accuracy is essential, such as medical diagnosis.
+
+In summary, although adversarial training has made significant progress in improving adversarial robustness, its limitations—such as weak generalization, high training overhead, and performance degradation on clean data—necessitate further research and refinement.
+
 {\small

### 2025-05-24 AIAA2290/Proj-examples/freelb.py

@@ -1,0 +1,83 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import lib.perturb as perturb
+from torch.utils.data import DataLoader
+from tensorboardX import SummaryWriter
+from tqdm import tqdm
+import pgdattack
+
+def train(
+        model : nn.Module,
+        train_loader : DataLoader,
+        test_loader : DataLoader,
+        epochs : int,
+        lr : float,
+        num_iterate : int,
+        num_attack_iterate : list[int],
+        epsilon : float,
+        alpha : float,
+        logger : SummaryWriter,
+        model_name : str,
+) :
+    optimizer = torch.optim.Adam(model.parameters(), lr=lr)
+
+   
+    for epoch in tqdm(range(epochs)) :
+            
+        acc_train, loss_train = 0, 0
+
+        
+
+        for i, (x, y) in enumerate(train_loader) :
+            x : torch.Tensor = x.cuda()
+            y : torch.Tensor = y.cuda()
+            
+            x_a = x.data.clone()
+
+            optimizer.zero_grad()
+            for k in range(num_iterate) :
+                x_a = perturb.preturb(model, x, x_a, y, epsilon=epsilon, alpha=alpha, val_max=1, val_min=0)
+
+                y_pred : torch.Tensor = model(x_a, eval=False)
+                loss = F.cross_entropy(y_pred, y)
+                loss.backward()
+
+            for name, param in model.named_parameters() :
+                param.grad /= num_iterate
+            optimizer.step()
+            
+
+            acc_train += (y_pred.argmax(1) == y.argmax(1)).sum().item()
+            loss_train += loss.sum().item()
+
+        acc_train /= len(train_loader) * train_loader.batch_size
+        loss_train /= len(train_loader) * train_loader.batch_size
+
+        logger.add_scalar(f"train/acc", acc_train, epoch + 1)
+        logger.add_scalar(f"train/loss", loss_train, epoch + 1)
+
+
+        for attack_iterate in num_attack_iterate :
+            pgdattack.test(
+                model=model,
+                epoch_id=epoch + 1,
+                test_loader=test_loader,
+                epsilon=epsilon,
+                alpha=alpha,
+                num_iterate=attack_iterate,
+                logger=logger,
+                logger_tag=f"test-{attack_iterate}"
+            )
+    model._save_to_state_dict(f"./model_pth/", prefix=model_name, keep_vars=True)
[…]

### 2025-05-24 AIAA2290/Proj-examples/main.py

@@ -2,6 +2,7 @@ import torch
 import models.cnn
 import data.mnist
 import pgd
+import freelb
 import argparse
 from tensorboardX import SummaryWriter
 
@@ -13,6 +14,7 @@ if __name__ == "__main__" :
     parse.add_argument("--num_iterate", type=int, default=40)
     parse.add_argument("--epsilon", type=float, default=0.3)
     parse.add_argument("--alpha", type=float, default=0.01)
+    parse.add_argument("--algorithm", type=str, default="pgd", choices=["pgd", "freelb"])
     parse.add_argument("log", type=str)
     
     args = parse.parse_args()
@@ -21,16 +23,31 @@ if __name__ == "__main__" :
     model = models.cnn.CNN(in_channels=1, num_classes=10).cuda()
     logger = SummaryWriter(f"run/{args.log}", flush_secs=1)
 
-    pgd.train(
-        model=model,
-        train_loader=train_loader,
-        test_loader=test_loader,
-        epochs=args.epochs,
-        lr=args.lr,
-        num_iterate=args.num_iterate,
-        num_attack_iterate=[0,10,40],
-        epsilon=args.epsilon,
-        alpha=args.alpha,
-        logger=logger,
-        model_name=args.log
-    )
+    if args.algorithm == "pgd" :
+        pgd.train(
+            model=model,
+            train_loader=train_loader,
+            test_loader=test_loader,
+            epochs=args.epochs,
+            lr=args.lr,
+            num_iterate=args.num_iterate,
+            num_attack_iterate=[0,10,40],
+            epsilon=args.epsilon,
+            alpha=args.alpha,
+            logger=logger,
+            model_name=args.log
+        )
+    elif args.algorithm == "freelb" :
+        freelb.train(
+            model=model,
+            train_loader=train_loader,
+            test_loader=test_loader,
+            epochs=args.epochs,
+            lr=args.lr,
+            num_iterate=args.num_iterate,
+            num_attack_iterate=[0,10,40],
+            epsilon=args.epsilon,
+            alpha=args.alpha,
+            logger=logger,
+            model_name=args.log
+        )

### 2025-05-25 AIAA2290/report/main.tex
Finish report of AIAA2290

@@
 \author{Jiarui HE\\
-50013538 \\
+College of Education Sciences \\
+The Hong Kong University of Science and Technology (Guangzhou) \\
 {\tt\small jhe218@connect.hkust-gz.edu.cn}
@@
 \begin{abstract}
-This report examines the inherent challenges and limitations of adversarial training for neural networks.
-We highlight issues related to generalization, computational complexity, and performance trade-offs, and discuss potential directions for future research.
+Adversarial examples—small, intentionally crafted perturbations to input data—pose a critical threat to the reliability of modern machine learning models.
+In this report, we first review the theoretical foundations of adversarial robustness, formalizing the min-max optimization objective that underlies adversarial training.
+We then survey prominent attack and defense algorithms, including Projected Gradient Descent (PGD), and the FreeLB framework.
+To assess practical performance, we conduct an empirical study on a lightweight seven-layer convolutional network, comparing standard training against PGD- and FreeLB-based adversarial training under varying perturbation intensities.
+Our results show that multi-step adversarial training increases robust accuracy from roughly 56\% to over 95\% under strong PGD attacks, while incurring a modest decrease in clean-data accuracy and a significant rise in training time.
+Then, we discuss the principal challenges—namely, the robustness-accuracy trade-off, high computational cost.
+Finally, we discuess the further application of adversarial training and related concepts, including GANs and Adversarial Explainability.
 \end{abstract}
@@
 Subsequent techniques often build upon PGD, introducing modifications to improve efficiency, convergence, or transferability.
-Additionally, adversarial training has been integrated into generative frameworks such as Generative Adversarial Networks (GANs) to further enhance model robustness.
 
@@
         \State {execute backpropagation}
-        \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_{\theta}(\mathrm{X}+\delta), y))$
+        \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_{\theta}(\mathrm{X}+\delta), \mathbf{y}))$
         \State $\delta\leftarrow \mathrm{clamp}(\delta + \frac{\alpha}{\left\lVert g_a \right\rVert}g_a, -\epsilon, \epsilon)$
       \EndFor
-      \State $g_\theta\leftarrow \nabla_{\theta}(L(f_{\theta}(\mathrm{X}+\delta), y))$
+      \State $g_\theta\leftarrow \nabla_{\theta}(L(f_{\theta}(\mathrm{X}+\delta), \mathbf{y}))$
       \State $\theta \leftarrow \theta - \tau g_\theta$
@@
 
-This training methods aims to enhance the efficiency of training by reducing the frequency of entire backpropagation.
-According to the pontryagin maximum principle (PMP), this algorithm assumes that the model mainly use the first layer to handle the attack.
-Thus, the process of gradient calculation can reuse the gradients excepts the first layer.
+The YOPO algorithm aims to improve computational efficiency during adversarial training by reducing the number of full backpropagation operations.
+Leveraging insights from the Pontryagin Maximum Principle (PMP), YOPO posits that the model's first layer is primarily responsible for responding to adversarial perturbations.
+Based on this assumption, the algorithm reuses gradients for all layers except the first across multiple inner-loop iterations.
 
-Training on one mini-batch is an $m\times n$ loop, where $m, n$ are both hyperparameters.
-In the outer loop, program will execute the entire backpropagation once and get the gradients of the layers excepts the first, then execute the inner loop to calculate the gradient of the first layer and iterate the attack sample.
-A YOPO process with specific $m, n$ is noted by YOPO-$m$-$n$ .
+In this framework, each mini-batch is processed through a two-level loop structure defined by hyperparameters $m$ and $n$.
+The outer loop executes full backpropagation once to compute gradients for all layers except the first.
+Within the inner loop, adversarial perturbations are iteratively updated using gradients computed only for the first layer.
+The configuration is denoted as YOPO-$m$-$n$.
 
-The pesuado code of this algorirthm is shown below:
+The pseudocode for this method is presented below:
 
@@
 \end{breakablealgorithm}
-For one mini-batch, entire backpropagation is executed only for $\Theta(m)$ times, however, the number of iterations of attack sample is $\Theta(mn)$ .
-Additionally, according to the paper by Zhang D, et.
-al.
-\cite{zhang2019propagateonceacceleratingadversarial} .
-When $m\times n$ is slightly larger than $k$ , then YOPO-$m$-$n$ can achieve similar performance with PGD-$k$ .
 
-However, there are analysis \cite{zhu2020freelbenhancedadversarialtraining} which claims that the PMP-based assumption does not hold on ReLU-based models.
+In this scheme, full backpropagation is performed only $\mathcal{O}(m)$ times per mini-batch, whereas adversarial example updates occur $\mathcal{O}(mn)$ times.
+According to Zhang et al.~\cite{zhang2019propagateonceacceleratingadversarial}, if $m \times n$ slightly exceeds $k$, YOPO-$m$-$n$ can achieve comparable performance to PGD-$k$ with significantly reduced computational cost.
+
+Nonetheless, other analyses~\cite{zhu2020freelbenhancedadversarialtraining} suggest that the PMP-based assumptions underlying YOPO may not hold in models utilizing ReLU activation functions.
 
@@
 
-Different from that PGD iterates the attack sample for $k$ times and only apply it to update the model with the final sample, FreeLB use average to use all the samples in iteration process.
+ifferent from PGD, which performs $k$ iterations to generate an adversarial example and uses only the final perturbed sample to update the model, FreeLB aggregates the gradient contributions from all intermediate perturbations by averaging them.
+This strategy leverages the full spectrum of adversarial information encountered during the iterative process.
 
-This algorithm can be treated as a case of YOPO when we set $n=1$ , but it can work on ReLU-bases models.
+FreeLB can be viewed as a special case of YOPO when the number of inner iterations $m$ is set to 1.
+Unlike YOPO, however, FreeLB is also applicable to models employing ReLU activations, which are common in modern architectures.
 
-Here is a comparison with PGD: The process of PGD is to find a attack sample by multiple maximization of the loss function, then minimize the loss once by gradient descent.
-FreeLB, however, minimizes the loss after each miximization operation.
-This modify can increase the robustness and increase the performance of training \cite{zhu2020freelbenhancedadversarialtraining} .
+In contrast to PGD, which first performs multiple inner maximizations to generate a strong adversarial example and then applies a single gradient descent update on the model parameters, FreeLB interleaves the two processes.
+Specifically, it performs model updates after each inner-loop maximization step.
+This interleaved optimization approach has been shown to improve both model robustness and training efficiency~\cite{zhu2020freelbenhancedadversarialtraining}.
 
-The pesuado code of this algorirthm is shown below:
+The pseudocode for the FreeLB training procedure is as follows:
 
@@
 
-However, conducting of entire backpropagation and gradient accumulation for each iteration may cause high time consumption. And this will be shown on \cref{table:instance_training-result}
+However, it is important to note that performing full backpropagation and accumulating gradients at each inner-loop iteration incurs higher computational cost.
+This computational overhead is empirically demonstrated in Table~\ref{table:instance_training-result}.
 
@@
 
-This algorithm does not aim to achieve the target shown above (\cref{eq:adv_training_objective}) , but treats the preturbation as regularization item.
-It attempts to guide the model to output the same prediction for adjacent samples.
-And this algorithm is shown to be effective for fine-tuning of pre-trained natural language processing model \cite{Jiang_2020} .
+Unlike traditional adversarial training approaches that directly aim to optimize the objective defined in Equation~\ref{eq:adv_training_objective}, this algorithm treats adversarial perturbations as a form of regularization.
+Specifically, it encourages the model to produce consistent predictions for inputs within a small neighborhood in the input space.
+This regularization-based adversarial training paradigm has been shown to be particularly effective for fine-tuning pre-trained language models in natural language processing tasks~\cite{Jiang_2020}.
 
-The target formula is shown below :
+The corresponding optimization objective is defined as follows:
 
 \begin{equation}
-  \theta^*=\arg\min_\theta\{\mathcal{L}(\theta)+\lambda \mathcal{R}(\theta)\}
+\theta^* = \arg\min_\theta\left\{\mathcal{L}(\theta) + \lambda \mathcal{R}(\theta)\right\}
 \tag{2:4:1}
@@
 \end{equation}
-where $\mathcal{L}(\theta)$ is the sum of loss of the original dataset, $\lambda$ is the hyperparameter that $\lambda>0$ and $\mathcal{R}(\theta)$ is the smoothness-inducing adversarial regularizer.
+
+Here, $\mathcal{L}(\theta)$ denotes the empirical risk over the training dataset, $\lambda > 0$ is a hyperparameter balancing the two terms, and $\mathcal{R}(\theta)$ is a smoothness-inducing adversarial regularization term.
+The detailed formulations are given by:
 
@@
 
-and $l(a, b)$ is the symmetric KL divergence :
+The divergence measure $l(a, b)$ used in $\mathcal{R}(\theta)$ is the symmetric Kullback-Leibler (KL) divergence defined as:
 
@@
 
-To solve \cref{formula:adversarial_target2} , Bregman proximal point optimization is applied, the key function of this algorithm is called Bregman divergence:
+To optimize the objective in Equation~\ref{formula:adversarial_target2}, the algorithm adopts a Bregman proximal point optimization framework.
+The core component of this framework is the Bregman divergence, defined over dataset $\mathcal{D}$ as:
 
@@
 
-Then for each mini-batch, algorithm applied this function as the loss function to iterate the attack sample.
-For more precisely, the formula of gradient of attack sample perturbation $\delta$ on dataset $\mathcal{D}$ is defined as :
+For each mini-batch, this divergence serves as a surrogate loss to guide the generation of adversarial perturbations.
+More specifically, the gradient of the perturbation $\delta$ for a mini-batch $\mathcal{D}$ is computed as follows:
 
@@
 
-Furthermore, this algorihtm applies momentum and Adam update rule for optimizing. Here is the pesuado code:
+To further enhance optimization stability and convergence, momentum and the Adam update rule are applied throughout the training process.
+The pseudocode outlining this algorithm will be presented below.
 
@@
 
-An instance of adversarial training is provided for better understanding of its features and evaluation, which includes the implementation of PGD and FreeLB.
+To provide a concrete illustration of adversarial training and facilitate analysis of its characteristics and effectiveness, we conducted empirical experiments using both PGD and FreeLB algorithms.
 
-We applied \texttt{torch} library for training and testing, while dataset is MNIST, which is a typical dataset for image recognition.
-And the GPU and CPU are RTX2080Ti-22G and Intel-13900K respectively.
+The experiments were implemented using the \texttt{torch} library.
+The dataset utilized was MNIST, a widely adopted benchmark for image classification tasks.
+The computational environment comprised an NVIDIA RTX 2080Ti GPU (22GB VRAM) and an Intel Core i9-13900K CPU.
 
-For hyperparameter setting, the learing rate are all $1\times 10^{-4}$ and the training epochs are all $50$. Rule of gradient updating is Adam.
+For all experiments, the learning rate was set to $1 \times 10^{-4}$, and the number of training epochs was fixed at 50. The Adam optimizer was employed for parameter updates.
 
-The model is a simple convolution nerual network, whose architecture is shown below:
+The model used was a lightweight convolutional neural network, whose architecture is summarized in Table~\ref{table:instance_model-arch}:
 
@@
 
-The result shows some features and drawbacks of adversarial training.
+The results reveal several key insights into adversarial training:
 
-For one thing, the accuracy of recognition by models after adversarial training on original sample is lower than that trained with original dataset.
-Furthermore, the increase of number of iteration for generation of training attack sample, which corresponds to the increase of perturbation intensity, leads to the worse performance on original dataset.
+First, models trained with adversarial examples tend to exhibit slightly reduced performance on clean (unperturbed) test data compared to those trained under standard conditions.
+This performance drop becomes more pronounced as the number of inner-loop adversarial iterations increases, which correlates with the intensity of the applied perturbations.
 
-For another thing, the increase time consumption for adversarial training is also be considered in practical application.
+Second, adversarial training introduces significant computational overhead.
+As shown in Table~\ref{table:instance_training-result}, the training time increases considerably with the number of adversarial steps.
+This trade-off between robustness and training efficiency is an important consideration in practical deployment scenarios.
 
@@
 Lechner et al.~\cite{lechner2021adversarialtrainingreadyrobot} demonstrated that AT can introduce new risks in robotic learning systems, including transient errors, systemic biases, and conditional failures.
-These issues suggest that in dynamic and complex environments, AT may compromise the model’s stability and interpretability.
+These issues suggest that in dynamic and complex environments, AT may compromise the model's stability and interpretability.
 
@@
 Adversarial training often comes at the cost of reduced accuracy on clean (non-adversarial) inputs.
-Zhao et al.~\cite{a15080283} observed in their systematic review that this "robustness–accuracy trade-off" is a central challenge in current AT methods, and can be particularly problematic in domains where high accuracy is essential, such as medical diagnosis.
+Zhao et al.~\cite{a15080283} observed in their systematic review that this "robustness-accuracy trade-off" is a central challenge in current AT methods, and can be particularly problematic in domains where high accuracy is essential, such as medical diagnosis.
+The result of training instance on \cref{table:instance_training-result} indicates this issues by that the accuracy of comparison of standard training and PGD-40 training.
 
 In summary, although adversarial training has made significant progress in improving adversarial robustness, its limitations—such as weak generalization, high training overhead, and performance degradation on clean data—necessitate further research and refinement.
+
+\section{Further Applications}
+
+Adversarial training has proven to be a versatile framework beyond its original role in enhancing model robustness against malicious perturbations.
+In particular, it underpins two prominent domains: generative modeling—most notably Generative Adversarial Networks (GANs)—and adversarial explainability, which leverages adversarial perturbations to illuminate the decision-making processes of complex models.
+
+\subsection{Generative Modeling via Adversarial Games}
+
+In the context of generative modeling, adversarial training formulates a two-player minimax optimization between a \emph{generator} $G$ and a \emph{discriminator} $D$.
+Given a noise prior $z\sim p_z(z)$ and real data distribution $x\sim p_{\mathrm{data}}(x)$, the objective is
+
+$$
+\begin{aligned}
+\min_{G} &\max_{D} V(D,G)= \\
+& \mathbb{E}_{x\sim p_{\mathrm{data}}}\bigl[\log D(x)\bigr]
+\;+\;\mathbb{E}_{z\sim p_z}\bigl[\log\bigl(1 - D(G(z))\bigr)\bigr]
+\end{aligned}
+$$
+
+Here, $D$ aims to accurately distinguish genuine samples from synthetic ones $G(z)$, while $G$ seeks to generate data that aligns with the empirical distribution.
+At equilibrium, $G$ reproduces the data distribution and $D$ attains maximal entropy ($D(\cdot)=0.5$) \cite{goodfellow2014generativeadversarialnetworks}.
+Variants such as Wasserstein GANs (WGAN) and Deep Convolutional GANs (DCGAN) have been developed to improve optimization stability and sample fidelity.
+
+\subsection{Adversarial Explainability}
+
+Adversarial explainability uses perturbation analysis to explore model interpretability.
+For a classifier $f: \mathbb{R}^n\to{1,\dots,K}$ and input $x$, one determines the minimal perturbation $\delta$ that alters the predicted label:
+
+$$
+\begin{aligned}
+\delta^* &= \arg\min_{\|\delta\|\le\epsilon} \|\delta\| \\
+\text{s.t.}&\quad
+\arg\max_x f(x+\delta) \neq \arg\max_x f(x)
+\end{aligned}
+$$
+
+The vector $\delta^*$ highlights input dimensions critical to the decision boundary: components with larger magnitude indicate features to which $f$ is most responsive.
+Such perturbations can be visualized as sensitivity maps or quantified as feature importance scores, thereby elucidating the model's reliance on specific input characteristics \cite{NEURIPS2019_e2c420d9, tsipras2019robustnessoddsaccuracy}.
+
+\medskip
+In summary, adversarial training serves a dual purpose: as a generative mechanism producing high-quality synthetic samples, and as a diagnostic tool revealing the sensitivities of neural models.
+Its formulation as minimax optimization provides a unified theoretical foundation for both applications.
+
+\section{Conclusion}
+
+In this report, we have presented a comprehensive exploration of adversarial training, beginning from its theoretical underpinnings to practical algorithmic implementations.
+We formally defined the robust optimization objective and surveyed state-of-the-art methods including PGD-based training and FreeLB.
+Through a controlled empirical study on a lightweight convolutional neural network, we demonstrated that adversarial training markedly enhances model robustness—elevating accuracy under strong perturbations from approximately 56\% to over 95\%—while incurring only a modest reduction in clean-data performance.
+We also highlighted the substantial computational overhead introduced by multi-step adversarial methods, which poses a significant barrier to large-scale deployment.
+
+Despite these challenges, adversarial training remains the most effective defense strategy against worst-case perturbations.
+Addressing its limitations requires future work in several directions: developing more efficient optimization schemes to reduce training time, designing adaptive perturbation strategies that balance robustness and accuracy, and extending adversarial frameworks to diverse modalities such as text and graph-structured data.
+Furthermore, deeper theoretical analyses are needed to understand the fundamental trade-offs between robustness, generalization, and computational complexity.
+By advancing both the practical and theoretical aspects of adversarial training, we can move closer to deploying machine learning models that are both high-performing and resilient in real-world, adversarial environments.
 

### 2025-05-26 AIAA2290/Proj-examples/plot.py
Update report of AIAA2290

@@ -1,0 +1,85 @@
+from tensorboard.backend.event_processing import event_accumulator
+import matplotlib.pyplot as plt
+import numpy as np
+import os
+
+log_path = [
+	"freeLB-10",
+	"freeLB-40",
+	"PGD-10",
+	"PGD-40",
+	"std"
+]
+log_label = [
+	"FreeLB-10",
+	"FreeLB-40",
+	"PGD-10",
+	"PGD-40",
+	"Standard"
+]
+
+# also the name of figure file
+items = [
+	("test-0", "Original"),
+	("test-10", "PGD-10 Attack"),
+	("test-40", "PGD-40 Attack"),
+	("train", "Training")
+]
+
+subitems_idx = {
+	"acc" : 0,
+	"loss" : 1
+}
+
+ylim = {
+	"acc" : (0.7, 1.0),
+	"loss" : (0, 0.058)
+}
+
+subitems_name = [
+	"accuracy",
+	"loss"
+]
+
+def getEventAccumulator(log_path : str) -> event_accumulator.EventAccumulator:
+	files = os.listdir(os.path.join("run", log_path))
+	if len(files) == 0:
+		print(f"No files found in {log_path}")
+		return None
+	# get newest file
+	ea = event_accumulator.EventAccumulator(os.path.join("run", log_path))
+	ea.Reload()
+	return ea
+
+if __name__ == "__main__":
+	# create 4 subplots for each item
+	figs = [plt.subplots(nrows=1, ncols=2, figsize=(10, 6)) for _ in range(len(items))]
+	
+	for fig, ax in figs :
+		for (tag, subitem_idx) in subitems_idx.items() :
+			ax[subitem_idx].set_title(f"{subitems_name[subitem_idx]}")
+			ax[subitem_idx].set_xlabel("Steps")
+			ax[subitem_idx].set_ylabel(f"{tag.capitalize()}")
+			ax[subitem_idx].set_ylim(ylim[tag])
+			ax[subitem_idx].grid()
+
+	for i, (path, label) in enumerate(zip(log_path, log_label)) :
+		ea = getEventAccumulator(path)
+
+		for subitem_tag, subitem_idx in subitems_idx.items() :
+			for i, item in enumerate(items) :
+				fig, ax = figs[i]
+				dtList = ea.scalars.Items(f"{item[0]}/{subitem_tag}")
+				x = np.array([dt.step for dt in dtList])
[…]

### 2025-05-26 DSAA2011/merge.sh

@@ -6,6 +6,7 @@ pandoc \
     note-decisiontree.md \
     note-ensemble.md \
     note-cluster.md \
+    note-kernel.md \
     -o note.pdf \
     --pdf-engine=xelatex \
     --toc \

### 2025-05-26 AIAA2290/report/main.tex
Update report of AIAA2290
Update ...

@@
 \usepackage{multirow}
+\usepackage{graphicx}
 
@@
 \theta^*=\arg\min_\theta\left\{
-  \mathbb{E}_{(\mathbf{x}, \mathbf{y})\in \mathcal{D}}
+  \mathbb{E}_{(\bf{x}, \bf{y})\in \mathcal{D}}
   \left[
-      \max_{\lVert\mathbf{\delta}\rVert\leq \epsilon}
-          \left\{L(f_\theta(\mathbf{x}+\delta), y)\right\}
+      \max_{\lVert\bf{\delta}\rVert\leq \epsilon}
+          \left\{L(f_\theta(\bf{x}+\delta), y)\right\}
   \right]
@@
 \begin{equation}
-\theta^{*} = \arg\min_{\theta} ; \mathbb{E}{(\mathbf{x},\mathbf{y}) \sim \mathcal{D}} \Biggl[\underbrace{\max_{{\lVert \mathbf{\delta} \rVert \le \epsilon}} L\bigl(f_{\theta}(\mathbf{x} + \mathbf{\delta}), \mathbf{y}\bigr)}_{\text{worst-case loss}}\Biggr]
+\theta^{*} = \arg\min_{\theta} ; \mathbb{E}{(\bf{x},\bf{y}) \sim \mathcal{D}} \Biggl[\underbrace{\max_{{\lVert \bf{\delta} \rVert \le \epsilon}} L\bigl(f_{\theta}(\bf{x} + \bf{\delta}), \bf{y}\bigr)}_{\text{worst-case loss}}\Biggr]
 \label{eq:adv_training_objective}
@@
 
-Here, the inner maximization identifies the most adversarial perturbation $\mathbf{\delta}$ within the $\epsilon$-ball around the input $\mathbf{x}$, while the outer minimization optimizes the model parameters to minimize the expected worst-case loss over the data distribution $\mathcal{D}$.
+Here, the inner maximization identifies the most adversarial perturbation $\bf{\delta}$ within the $\epsilon$-ball around the input $\bf{x}$, while the outer minimization optimizes the model parameters to minimize the expected worst-case loss over the data distribution $\mathcal{D}$.
 
@@
 \begin{aligned}
-\mathbf{\delta}_{0} &= \mathbf{0}, \\
-\mathbf{\delta}_{t+1} &= \Pi_{{\lVert \mathbf{\delta_t} \rVert \le \epsilon}} \Bigl(\mathbf{\delta}_{t} + \alpha \cdot \mathrm{sign}\bigl(\nabla_{\mathbf{x}} L(f_{\theta}(\mathbf{x} + \mathbf{\delta}_{t}), \mathbf{y})\bigr)\Bigr),
+\bf{\delta}_{0} &= \bf{0}, \\
+\bf{\delta}_{t+1} &= \Pi_{{\lVert \bf{\delta_t} \rVert \le \epsilon}} \Bigl(\bf{\delta}_{t} + \alpha \cdot \mathrm{sign}\bigl(\nabla_{\bf{x}} L(f_{\theta}(\bf{x} + \bf{\delta}_{t}), \bf{y})\bigr)\Bigr),
 \end{aligned}
@@
 
-After $k$ iterations, the adversarial example is given by $\mathbf{x}^{\mathrm{adv}} = \mathbf{x} + \mathbf{\delta}_{k}$.
+After $k$ iterations, the adversarial example is given by $\bf{x}^{\mathrm{adv}} = \bf{x} + \bf{\delta}_{k}$.
 Incorporating these examples into the training process yields the PGD adversarial training algorithm
@@
   \For {$n=1$ to $N$}
-    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \mathbf{y})\}$}
-    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}$} 
+    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \bf{y})\}$}
+    \For {$(\mathrm{X}, \bf{y})\in \mathcal{C}$} 
       \State {$\delta\leftarrow$ zero matrix with shape of $X$}
@@
         \State {execute backpropagation}
-        \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_{\theta}(\mathrm{X}+\delta), \mathbf{y}))$
+        \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_{\theta}(\mathrm{X}+\delta), \bf{y}))$
         \State $\delta\leftarrow \mathrm{clamp}(\delta + \frac{\alpha}{\left\lVert g_a \right\rVert}g_a, -\epsilon, \epsilon)$
       \EndFor
-      \State $g_\theta\leftarrow \nabla_{\theta}(L(f_{\theta}(\mathrm{X}+\delta), \mathbf{y}))$
+      \State $g_\theta\leftarrow \nabla_{\theta}(L(f_{\theta}(\mathrm{X}+\delta), \bf{y}))$
       \State $\theta \leftarrow \theta - \tau g_\theta$
@@
   \For {$i\leftarrow 1$ to $N$}
-    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \mathbf{y})\}$}
-    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}$}
+    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \bf{y})\}$}
+    \For {$(\mathrm{X}, \bf{y})\in \mathcal{C}$}
       \State $\delta_{0, n}\leftarrow \text{zero matrix with shape of } \mathrm{X}$
@@
         \State {$p\leftarrow \nabla_{f_{\theta_0}(\mathrm{X}+\delta_{j,0})}\left(
-          L(f_\theta(\mathrm{X}+\delta_{j,0}), \mathbf{y})
+          L(f_\theta(\mathrm{X}+\delta_{j,0}), \bf{y})
         \right)$}
@@
         \EndFor
-        \State $g_\theta\leftarrow g_\theta + \nabla_{\theta}(L(f_{\theta}(\mathrm{X}+\delta_{j,n}), \mathbf{y}))$
+        \State $g_\theta\leftarrow g_\theta + \nabla_{\theta}(L(f_{\theta}(\mathrm{X}+\delta_{j,n}), \bf{y}))$
         \Comment this gradient can be calculated in backpropagation
@@
   \For {$i\leftarrow 1$ to $N$}
-    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \mathbf{y})\}$}
-    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}$}
+    \State {divide $\mathcal{D}$ into list of mini-batches $\mathcal{C}=\{(\mathrm{X}, \bf{y})\}$}
+    \For {$(\mathrm{X}, \bf{y})\in \mathcal{C}$}
       \State $\delta_0\leftarrow \textbf{random}\text{ matrix with shape of } \mathrm{X}$
@@
         \State {execute backpropagation}
-        \State $g_\theta\leftarrow g_\theta + \frac{1}{k}\nabla_{\theta}(L(f_\theta(\mathrm{X}+\delta_{i-1}), \mathbf{y}))$
-        \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_\theta(\mathrm{X}+\delta_{i-1}), \mathbf{y}))$
+        \State $g_\theta\leftarrow g_\theta + \frac{1}{k}\nabla_{\theta}(L(f_\theta(\mathrm{X}+\delta_{i-1}), \bf{y}))$
+        \State $g_a\leftarrow \nabla_{\mathrm{X}+\delta}(L(f_\theta(\mathrm{X}+\delta_{i-1}), \bf{y}))$
         \State $\delta_i\leftarrow \mathrm{clamp}\left(\delta_{i-1}+\frac{\alpha}{\left\lVert g_a \right\rVert}g_a, -\epsilon, \epsilon\right)$
@@
 \begin{aligned}
-  &\mathcal{L}(\theta)=\frac{1}{n}\sum_{(\mathbf{x}, \mathbf{y})\in\mathcal{D}} L(f_\theta(\mathbf{x}), \mathbf{y}) \\
-  &\mathcal{R}(\theta)=\frac{1}{n}\sum_{(\mathbf{x}, \mathbf{y})\in\mathcal{D}} \max_{\left\Vert \tilde{\mathbf{x}}-\mathbf{x}\right\Vert\leq \epsilon}\left\{l\left(f_\theta(\tilde{\mathbf{x}}), f_\theta(\mathbf{x})\right)\right\}
+  &\mathcal{L}(\theta)=\frac{1}{n}\sum_{(\bf{x}, \bf{y})\in\mathcal{D}} L(f_\theta(\bf{x}), \bf{y}) \\
+  &\mathcal{R}(\theta)=\frac{1}{n}\sum_{(\bf{x}, \bf{y})\in\mathcal{D}} \max_{\left\Vert \tilde{\bf{x}}-\bf{x}\right\Vert\leq \epsilon}\left\{l\left(f_\theta(\tilde{\bf{x}}), f_\theta(\bf{x})\right)\right\}
 \end{aligned}
@@
 \begin{aligned}
-l(f, g)&=\mathrm{KL}(f\Vert g) + \mathrm{KL}(f\Vert g) \\
+l(f, g)&=\mathrm{KL}(f\Vert g) + \mathrm{KL}(g\Vert f) \\
 &=\sum_{x\in \mathcal{X}} f(x)\log\frac{f(x)}{g(x)} + g(x)\log\frac{g(x)}{f(x)} \\
@@
 \mathrm{Breg}_\mathcal{D}(\theta_1, \theta_2)=\frac{1}{\left\vert\mathcal{D}\right\vert}
-  \sum_{(\mathbf{x}, \mathbf{y})\in\mathcal{D}}l\left(f_{\theta_1}(\mathbf{x}), f_{\theta_2}(\mathbf{x})\right)
+  \sum_{(\bf{x}, \bf{y})\in\mathcal{D}}l\left(f_{\theta_1}(\bf{x}), f_{\theta_2}(\bf{x})\right)
 $$
@@
 \begin{bmatrix}
-  \nabla_{\delta_1}l(f_\theta(\mathbf{x}_1), f_\theta(\mathbf{x}_1+\delta_1)) \\
-  \nabla_{\delta_2}l(f_\theta(\mathbf{x}_2), f_\theta(\mathbf{x}_2+\delta_2)) \\
+  \nabla_{\delta_1}l(f_\theta(\bf{x}_1), f_\theta(\bf{x}_1+\delta_1)) \\
+  \nabla_{\delta_2}l(f_\theta(\bf{x}_2), f_\theta(\bf{x}_2+\delta_2)) \\
   \vdots \\
-  \nabla_{\delta_{|\mathcal{D}|}}l\left(f_\theta\left(\mathbf{x}_{|\mathcal{D}|}\right), f_\theta\left(\mathbf{x}_{|\mathcal{D}|}+\delta_{|\mathcal{D}|}\right)\right)
+  \nabla_{\delta_{|\mathcal{D}|}}l\left(f_\theta\left(\bf{x}_{|\mathcal{D}|}\right), f_\theta\left(\bf{x}_{|\mathcal{D}|}+\delta_{|\mathcal{D}|}\right)\right)
 \end{bmatrix}
@@
     \State {divide $\mathcal{D}$ into mini-batches $\mathcal{C}$}
-    \For {$(\mathrm{X}, \mathbf{y})\in \mathcal{C}$}
+    \For {$(\mathrm{X}, \bf{y})\in \mathcal{C}$}
       \State initialize $\delta$ with guassian distribution
@@
       \For {$i=1$ to $k$}
-        \State $g_i\leftarrow \frac{g_{\overline{\theta}}\left((\mathrm{X},\mathbf{y}), \delta\right)}{\left\Vert g_{\overline{\theta}}((\mathrm{X},\mathbf{y}), \delta) \right\Vert}$
+        \State $g_i\leftarrow \frac{g_{\overline{\theta}}\left((\mathrm{X},\bf{y}), \delta\right)}{\left\Vert g_{\overline{\theta}}((\mathrm{X},\bf{y}), \delta) \right\Vert}$
         \State $\delta\leftarrow \mathrm{clamp}(\delta + \alpha g_i, -\epsilon, \epsilon)$
       \EndFor
-      \State $\overline{\theta}\leftarrow \mathrm{Adam}\left(\overline{\theta}, (\mathrm{X}+\delta, \mathbf{y})\right)$
+      \State $\overline{\theta}\leftarrow \mathrm{Adam}\left(\overline{\theta}, (\mathrm{X}+\delta, \bf{y})\right)$
     \EndFor
@@
 \end{table}
+
+The record of training process is also provided :
+
+\begin{figure}[H]
+\centering
+\caption{Test With Original Samples}
+\includegraphics[width=0.45\textwidth]{figures/plot-Original.png}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\caption{Test With PGD-10}
+\includegraphics[width=0.45\textwidth]{figures/plot-PGD-10 Attack.png}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\caption{Test With PGD-40}
+\includegraphics[width=0.45\textwidth]{figures/plot-PGD-40 Attack.png}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\caption{On Training set}
+\includegraphics[width=0.45\textwidth]{figures/plot-Training.png}
+\end{figure}
 

### 2025-05-26 DSAA2011/merge.sh

@@ -7,6 +7,7 @@ pandoc \
     note-ensemble.md \
     note-cluster.md \
     note-kernel.md \
+    note-dimreduce.md \
     -o note.pdf \
     --pdf-engine=xelatex \
     --toc \

### 2025-05-27 DSAA2011/merge.sh
update note

@@ -8,6 +8,7 @@ pandoc \
     note-cluster.md \
     note-kernel.md \
     note-dimreduce.md \
+    note-graphmodel.md \
     -o note.pdf \
     --pdf-engine=xelatex \
     --toc \

### 2025-11-21 UCUG1702/assignment8.py
Add AIAA3111 assignments

@@ -1,0 +1,42 @@
+# 生成并显示蠕变试验中三种材料的应变-时间曲线图（单图）
+import numpy as np
+import matplotlib.pyplot as plt
+
+# 参数
+sigma0 = 1.0
+E_elastic = 1.0  # 理想弹性体的弹性模量，最终应变 = sigma0 / E_elastic = 1.0
+eta_viscous = 1.0  # 理想黏性体的黏度，斜率 = sigma0/eta = 1.0
+# 标准线性固体 (Zener) 参数（粘弹性聚合物示例）
+E1 = 2.0   # 串联弹簧（瞬时弹性）
+E2 = 5.0   # 并联弹簧（迟滞弹性）
+eta = 2.0  # 黏性元件粘度
+tau = eta / E2
+
+t = np.linspace(0, 5, 500)
+# 理想弹性固体：瞬时跳变到常数（在数值图中用极小时间模拟瞬时跳变）
+t_elastic = np.concatenate(([0.0, 1e-6], t[1:]))
+gamma_elastic = np.concatenate(([0.0, sigma0 / E_elastic], np.full(t.size-1, sigma0 / E_elastic)))
+
+# 理想牛顿流体：线性增长
+gamma_viscous = (sigma0 / eta_viscous) * t
+
+# 标准线性固体 (Zener)：瞬时弹性 + 指数趋近的迟滞部分
+gamma_visco = (sigma0 / E1) + (sigma0 / E2) * (1 - np.exp(-t / tau))
+
+# 绘图（单个子图）
+plt.figure(figsize=(8,5))
+plt.plot(t_elastic, gamma_elastic, label='理想胡克弹性固体（弹性）', linewidth=2)
+plt.plot(t, gamma_viscous, label='理想牛顿黏性流体（黏性）', linewidth=2)
+plt.plot(t, gamma_visco, label='粘弹性聚合物（标准线性固体）', linewidth=2)
+
+plt.xlabel('时间 t')
+plt.ylabel('应变 γ')
+plt.title('蠕变试验：应变 γ vs 时间 t（在 t=0 施加常应力 σ0）')
+plt.legend()
+plt.grid(True)
+plt.xlim(0, 5)
+plt.ylim(0, 1.2)
+plt.annotate('σ0/E (弹性体)', xy=(0.5, sigma0/E_elastic), xytext=(1.0, 1.02),
+             arrowprops=dict(arrowstyle='->', linewidth=0.8))
+plt.tight_layout()
+plt.show()

### 2025-12-04 UCUG1702/project/report/report.tex
Add report of UCUG1702

\documentclass{article}

\usepackage[a4paper, total={6in, 9in}]{geometry}

\title{Molecular Dynamics Study of Water Using the TIP4P/2005 Model}
\author{Jiarui HE \\ UCUG1702}

\begin{document}
\maketitle

\section{Introduction}
The liquid water present at the air–water interface plays a crucial role in atmospheric chemistry,environmental processes, and a wide range of technologies.1–5 The structure of this interface governs phenomena such as aerosol reactivity, droplet stability, and wettability. In the bulk liquid phase, each water molecule generally forms approximately four hydrogen bonds, giving rise to a tetrahedral network. At the interface, however, this network is disrupted on the vapor side, which reduces the average number of hydrogen bonds and induces a preferential orientation of molecular dipoles and O–H bonds relative to the surface normal. A characteristic feature of this interfacial region is the presence of dangling hydrogens, which do not participate in hydrogen bonding and typically point toward the vapor phase.

Despite the apparent simplicity of the water molecule, liquid water exhibits remarkable properties at its free surface, including high surface tension and complex temperature-dependent changes in interfacial structure. These macroscopic properties are ultimately governed by temperature induced rearrangements of the hydrogenbond network and the orientational structure of interfacial molecules. In this work, we investigate (i) the distribution of hydrogen bonds formed by water molecules, (ii) the corresponding OH angles and dangling-hydrogen distributions relative to the surface normal and (iii) analyze of micro-structure form by water moleculars. By analyzing the temperature dependence of hydrogen bonding and OH orientational ordering at the interface, we aim to provide a microscopic understanding of the molecular structure of water at the airwater interface
\section{Methodology}

Molecular dynamics (MD) simulations with realistic water models can resolve interfacial structure at molecular length scales. Here, we use classical MD of a TIP4P/2005 water slab, a model that reproduces key thermodynamic and interfacial properties over a broad temperature range to examine how the hydrogen-bond network evolves at $T= 280,300,320 \rm{K}$

\bibliographystyle{nature}

\end{document}

### 2025-12-04 UCUG1702/project/analysis_danglingH.py

@@ -1,0 +1,453 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+对 LAMMPS 水体系 (type=1: O, type=2: H) 分析 O–H 取向和悬挂氢 (dangling H)：
+
+- 用 O–H 距离识别水分子（每个 O 找 2 个 H）
+- 对每条 O–H 键：
+    * 计算与 z 轴的夹角 theta_OH_z（度）和 cos(theta_OH_z)
+    * 用几何判据判断该 H 是否作为 donor 参与氢键
+      (O_donor–O_acceptor 距离 < ROO_CUT 且 O–H···O 角 <= ANGLE_CUT)
+      如果对任一 acceptor 满足则认为“成键”，否则“悬挂”
+- 按 z (用 O 的 z 坐标) 分层，对时间取平均：
+    * 所有 H 的 <theta_OH_z>、<cos theta_OH_z>
+    * 悬挂 H 的 <theta_OH_z>、<cos theta_OH_z>
+    * 悬挂 H 占比 f_dangling(z)
+
+输出：
+  1) dangling_OH_orientation_z_timeavg.dat
+     列：
+       z_center[A]
+       H_all_count_sum_over_frames
+       avg_theta_all_deg
+       avg_cos_all
+       H_dangling_count_sum_over_frames
+       avg_theta_dangling_deg
+       avg_cos_dangling
+       fraction_dangling
+  2) 两张图：
+       dangling_OH_theta_z.png
+       dangling_OH_costheta_z.png
+"""
+
+import sys
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+# ========================= 可调参数 =========================
+
+# O–H 共价键识别
+R_OH_BOND_MAX = 1.2   # Å
+
+# 氢键判据
+ROO_CUT   = 3.5       # O_donor–O_acceptor 最大距离 (Å)
+ANGLE_CUT = 30.0      # O–H···O 角阈值 (deg) —— 越小越接近线性
+
+# z 方向分层厚度
+DZ = 1.0              # Å
+
+# 最多读取的帧数；None 或 0 表示所有帧
+MAX_FRAMES = None
+
+
+# ========================= 读取 LAMMPS 轨迹 =========================
+
+def iter_lammps_frames(filename):
+    with open(filename, "r") as f:
+        while True:
+            line = f.readline()
+            if not line:
+                break
+            if not line.startswith("ITEM: TIMESTEP"):
[…]

### 2025-12-04 UCUG1702/project/v4.py

@@ -1,0 +1,707 @@
+import matplotlib
+
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import numpy as np
+from tqdm import tqdm
+
+#data_path = 'example_data.lammpstrj'
+data_path = 'F:/university/UCUG1702/water 1/dump-surface.lammpstrj'
+#data_path = 'F:/university/UCUG1702/water 1/dump-surface-280.lammpstrj'
+#data_path = 'F:/university/UCUG1702/water 1/dump-surface-320.lammpstrj'
+
+# 沿 z 轴方向将体系分层（用于分析不同 z 高度的水分子取向）
+layer_num = 1000
+
+# 存储盒子边界的最大/最小坐标（后续从轨迹文件中读取）
+max_pos = None  # np.ndarray shape=(3,)
+min_pos = None  # np.ndarray shape=(3,)
+
+
+class H2O:
+    """水分子类，用于存储单个水分子的氧原子和两个氢原子坐标，并处理周期性边界问题"""
+
+    def __init__(self, 
+                 pO: np.ndarray, 
+                 pH1: np.ndarray, 
+                 pH2: np.ndarray,
+                 box_min: np.ndarray,
+                 box_max: np.ndarray) -> None:
+        """
+        初始化水分子坐标
+
+        参数:
+            pO: 氧原子坐标 (x,y,z)
+            pH1: 第一个氢原子坐标 (x,y,z)
+            pH2: 第二个氢原子坐标 (x,y,z)
+            box_min: 本帧盒子下界 (xlo, ylo, zlo)
+            box_max: 本帧盒子上界 (xhi, yhi, zhi)
+        """
+        # 保存本帧盒子边界
+        self.box_min = box_min.copy()
+        self.box_max = box_max.copy()
+
+        # 原子坐标
+        self.pO = pO.copy()
+        self.pH1 = pH1.copy()
+        self.pH2 = pH2.copy()
+
+        # 在 box 信息已知时做 PBC 修正
+        self.pH1 = self._fix_pH(self.pH1)
+        self.pH2 = self._fix_pH(self.pH2)
+
+    def _fix_pH(self, pH: np.ndarray) -> np.ndarray:
+        """
+        修正氢原子坐标以符合周期性边界条件
+
+        思路：如果氢原子与氧原子的差向量在某一维超过 box_length / 2，
+        就通过 ±box_length 把 H 拉回到与 O 最近的镜像（只平移一次）。
+
[…]

### 2025-12-04 UCUG1702/project/v6.py

@@ -1,0 +1,598 @@
+import matplotlib
+
+matplotlib.use("Agg")
+import matplotlib.pyplot as plt
+import numpy as np
+from tqdm import tqdm
+
+# ================== 盒子边界（由 calc_1_frame 使用） ==================
+max_pos = None  # np.ndarray shape=(3,)
+min_pos = None  # np.ndarray shape=(3,)
+
+
+class H2O:
+    """水分子类：存一个水分子的 O、H1、H2 坐标，并在初始化时做一次 PBC 修正。"""
+
+    def __init__(
+        self,
+        pO: np.ndarray,
+        pH1: np.ndarray,
+        pH2: np.ndarray,
+        box_min: np.ndarray,
+        box_max: np.ndarray,
+    ) -> None:
+        # 保存本帧盒子边界
+        self.box_min = box_min.copy()
+        self.box_max = box_max.copy()
+
+        # 原子坐标
+        self.pO = pO.copy()
+        self.pH1 = pH1.copy()
+        self.pH2 = pH2.copy()
+
+        # 在 box 信息已知时做 PBC 修正（只修 H，O 保持原坐标）
+        self.pH1 = self._fix_pH(self.pH1)
+        self.pH2 = self._fix_pH(self.pH2)
+
+    def _fix_pH(self, pH: np.ndarray) -> np.ndarray:
+        """
+        修正氢原子坐标以符合周期性边界条件：
+        如果 H 相对 O 在某一维度的差值超过 box_length/2，就 ±box_length 拉回最近镜像。
+        """
+        p = pH.copy()
+        for i in range(3):
+            box = self.box_max[i] - self.box_min[i]
+            if box <= 0:
+                continue
+
+            delta = p[i] - self.pO[i]
+
+            if delta > box / 2:
+                p[i] -= box
+            elif delta < -box / 2:
+                p[i] += box
+
+        return p
+
+
+def calc_1_frame(
+    data_raw: list[str], h2o_num: int, data_start_line: int
+) -> tuple[list[H2O], np.ndarray, np.ndarray]:
+    """
+    解析单个时间帧的数据，将原子坐标组装成水分子对象列表
+
+    参数:
+        data_raw: 当前帧的所有行（header + 原子行）
+        h2o_num: 水分子数量（每个水分子包括 3 个原子）
+        data_start_line: 当前帧在 data_raw 中的起始行号（一般为 0）
+    """
+    global min_pos, max_pos
+
[…]

### 2025-12-05 UCUG1702/project/report/report.tex
Modify of UCUG1702 report

@@
 \documentclass{article}
+\usepackage{unicode-math}  % <- 使 math 支持 Unicode
+\usepackage{amsmath}
+\usepackage{fontspec}
+\usepackage{geometry}
+\setmainfont{Times New Roman}
+\linespread{1.12}
+\usepackage{graphicx}
+\usepackage[backend=biber,style=nature,sorting=none]{biblatex}
+\addbibresource{report.bib} % 你的 bib 文件
 
-\usepackage[a4paper, total={6in, 9in}]{geometry}
+\setlength{\parindent}{0pt} % 取消所有段落的首行缩进
+\geometry{
+	a4paper,
+	includehead=true,
+	includefoot=true,
+	top=1in,
+	bottom=1in,
+	left=1in,
+	right=1in
+}
+\setlength{\parskip}{0.5\baselineskip}
 
@@
 \section{Introduction}
-The liquid water present at the air–water interface plays a crucial role in atmospheric chemistry,environmental processes, and a wide range of technologies.1–5 The structure of this interface governs phenomena such as aerosol reactivity, droplet stability, and wettability.
-In the bulk liquid phase, each water molecule generally forms approximately four hydrogen bonds, giving rise to a tetrahedral network.
-At the interface, however, this network is disrupted on the vapor side, which reduces the average number of hydrogen bonds and induces a preferential orientation of molecular dipoles and O–H bonds relative to the surface normal.
-A characteristic feature of this interfacial region is the presence of dangling hydrogens, which do not participate in hydrogen bonding and typically point toward the vapor phase.
+The air–water interface plays a key role in atmospheric chemistry, environmental processes, and various technologies.\cite{bonn2009wetting}\cite{butt2023interfaces}\cite{delapuente2023acidity}\cite{israelachvili2011intermolecular} Its structure governs aerosol reactivity, droplet stability, and wettability.
+In bulk water, each molecule typically forms about four hydrogen bonds, creating a tetrahedral network.
+At the interface, this network is disrupted toward the vapor side, reducing hydrogen-bond counts and inducing preferential orientation of molecular dipoles and O–H bonds.
+A notable feature is the presence of dangling hydrogens that point toward the vapor phase.
 
-Despite the apparent simplicity of the water molecule, liquid water exhibits remarkable properties at its free surface, including high surface tension and complex temperature-dependent changes in interfacial structure.
-These macroscopic properties are ultimately governed by temperature induced rearrangements of the hydrogenbond network and the orientational structure of interfacial molecules.
-In this work, we investigate (i) the distribution of hydrogen bonds formed by water molecules, (ii) the corresponding OH angles and dangling-hydrogen distributions relative to the surface normal and (iii) analyze of micro-structure form by water moleculars.
-By analyzing the temperature dependence of hydrogen bonding and OH orientational ordering at the interface, we aim to provide a microscopic understanding of the molecular structure of water at the airwater interface
+Despite water's simple molecular structure, its free surface exhibits remarkable properties such as high surface tension and temperature-dependent structural changes.
+These macroscopic behaviors stem from temperature-induced rearrangements of the hydrogen-bond network and interfacial molecular orientation.
+In this work, we investigate (i) the distribution of hydrogen bonds, (ii) OH angles and dangling-hydrogen profiles relative to the surface normal, and (iii) the local microstructure formed by water molecules.
+By analyzing temperature effects, we aim to provide a microscopic understanding of water's interfacial structure.
 \section{Methodology}
 
-Molecular dynamics (MD) simulations with realistic water models can resolve interfacial structure at molecular length scales.
-Here, we use classical MD of a TIP4P/2005 water slab, a model that reproduces key thermodynamic and interfacial properties over a broad temperature range to examine how the hydrogen-bond network evolves at $T= 280,300,320 \rm{K}$
+Molecular dynamics (MD) simulations with realistic water models can resolve interfacial structure at molecular scales.
+Here, we use classical MD of a TIP4P/2005 water slab—a model that reproduces key thermodynamic and interfacial properties across a broad temperature range—to examine hydrogen-bond network evolution at $T = 280,\;300,\;320\;\rm{K}$.
 
-\bibliographystyle{nature}
+From trajectories of 2000 configurations at each temperature, we compute the time-averaged number of hydrogen bonds per molecule along the surface normal ($z$-axis).
+We also calculate the dipole–normal angle and identify non‑hydrogen‑bonded (dangling) hydrogens to obtain $\langle\cos\theta_{\mathrm{OH}}(z)\rangle$ and the dangling-hydrogen fraction.
+These allow comparisons between bulk and interfacial regions and clarify how temperature modulates hydrogen-bond connectivity and dangling-hydrogen populations.
+Additionally, we analyze the angle distribution between molecules that share hydrogen bonds with a common molecule to probe interfacial microstructure.
+
+\subsection{Simulation setup}
+
+We simulated a slab of liquid water surrounded by vapor in a rectangular box with periodic boundary conditions in all three dimensions.
+The system contained 1056 TIP4P/2005 water molecules\cite{abascal2005tip4p2005}, arranged in a slab geometry at the box center.
+Box lengths were $L_x = L_y \approx 28.3\;\text{\AA},\; L_z \approx 80.0\;\text{\AA}$.
+The liquid occupied the central region along $z$, while the top and bottom regions remained empty.
+The slab geometry at the three temperatures is shown in Figure \ref{fig:slab}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.2]{slab.png}
+	\caption{Slab geometry of the TIP4P/2005 water model. Red spheres: oxygen atoms; blue spheres: hydrogen atoms.}
+	\label{fig:slab}
+\end{figure}
+
+\subsection{Reconstruction of water molecules}
+
+We reconstruct water molecules by fixing oxygen positions and adjusting hydrogen positions to recover ideal geometry from periodic simulation data.
+To correct for atoms that may map to the opposite side, components of $\overrightarrow{OH}$ vectors are compared with half the box lengths to determine proper hydrogen positions.
+
+\subsection{Hydrogen-bond analysis along $z$-axis}
+\label{sec:hb_analysis}
+
+Let $v_{\text{AB}}$ be the vector from atom A to atom B.
+
+Hydrogen bonds are identified using a geometric criterion: For a donor molecule D and an acceptor A (with atoms $\mathrm{O}_A, \mathrm{H}_{A_1}, \mathrm{H}_{A_2}$ and $\mathrm{O}_D$), a hydrogen bond exists if both conditions are satisfied:
+$$
+\begin{aligned}
+\left\Vert v_{\mathrm{O}_D \mathrm{O}_A} \right\Vert &< 3.5 \;\text{\AA} \\
+\min_{i=1,2}\left\{\left\langle v_{\mathrm{O}_D \mathrm{H}_{D,i}}, v_{\mathrm{H}_{D,i}\mathrm{O}_A}\right\rangle\right\} &\leq 30^{\circ}
+\end{aligned}
+$$
+To compute the average number of hydrogen bonds per molecule, the simulation box is divided uniformly into $40$ bins along $z$.
+Each molecule is assigned to a bin based on its oxygen atom’s $z$-coordinate.
+For each frame $f$, we calculate
+$$
+n^f_{\mathrm{HB}}(i)=\frac{\sum_{m \in \text{bin}_i} n_{\mathrm{HB}}(m)}{\left|\{m \in \text{bin}_i\}\right|},
+$$
+the average number of hydrogen bonds per molecule in bin $i$. Averaging over all frames gives $n_{\mathrm{HB}}(z_i)$, the position-dependent hydrogen-bond count.
+
+\subsection{O-H orientation and dangling hydrogen analysis}
+
+The orientation of O–H bonds relative to the surface normal is characterized by the angle $\theta_{\mathrm{OH}}$ between the O–H vector and the $z$-axis.
+For each water molecule, $\cos\theta_{\mathrm{OH}}$ is computed for both O–H bonds:
+$$
+\cos \theta_{\mathrm{OH}}=\frac{v_{\text{OH}}\cdot (0,0,1)^\top}{\left\Vert v_{\text{OH}}\right\Vert}.
+$$
+A hydrogen is considered dangling if no acceptor satisfies the hydrogen-bond criteria in Section~\ref{sec:hb_analysis}.
+
+The dipole angle $\theta_{\text{dipole}}$ between the molecular dipole vector and the $z$-axis is also computed. The dipole vector points from oxygen to the midpoint between the two hydrogens, with
+$$
+\cos \theta_{\text{dipole}}=\frac{v_{\text{dipole}}\cdot (0,0,1)^\top}{\left\Vert v_{\text{dipole}}\right\Vert},
+\qquad v_{\text{dipole}} = \frac{1}{2}\left(v_{\text{OH}_1} + v_{\text{OH}_2}\right).
+$$
+
+These values are binned according to the oxygen’s $z$-coordinate (using $500$ bins). For each bin $i$ in frame $f$:
+$$
+\begin{aligned}
+\theta_{\text{dipole}}^f(i) &= \frac{\sum_{m \in \text{bin}_i} \theta_{\text{dipole}}(m)}{|\{m \in \text{bin}_i\}|} \\
+\theta_{\text{dangling}}^f(i) &= \frac{\sum_{\substack{\text{OH} \in \text{bin}_i \\ \text{H dangling}}} \theta_{\text{OH}}}{\sum_{\substack{\text{OH} \in \text{bin}_i \\ \text{H dangling}}} 1} \\
+\theta_{\text{all}}^f(i) &= \frac{\sum_{\text{OH} \in \text{bin}_i} \theta_{\text{OH}}}{\sum_{\text{OH} \in \text{bin}_i} 1} \\
+\text{frac}^f_{\text{dangling}}(i) &= \frac{\sum_{\substack{\text{OH} \in \text{bin}_i \\ \text{H dangling}}} 1}{\sum_{\text{OH} \in \text{bin}_i} 1}
+\end{aligned}
+$$
+Averaging over all frames yields final profiles as functions of position.
+
+\subsection{Micro-structure analysis}
+
+For each molecule C, let $\{A_i\}$ be the set of molecules hydrogen‑bonded to C.
+For each unique pair $(A_i, A_j)$ in this set, compute the angle $\phi_{ij}$ between vectors $v_{\mathrm{O}_C \mathrm{O}_{A_i}}$ and $v_{\mathrm{O}_C \mathrm{O}_{A_j}}$.
+The average angle for molecule C is
+$$
+\phi_C = \frac{2}{N(N-1)} \sum_{i<j} \phi_{ij},
+$$
+where $N$ is the number of acceptors in $\{A_i\}$.
+These $\phi_C$ values are binned by the oxygen’s $z$-coordinate (40 bins) and scattered to visualize the angular distribution, revealing interfacial microstructure.
+
+\section{Results and Discussion}
+
+\subsection{Results}
+
+\subsubsection{Hydrogen-bond profile along $z$-axis}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.3]{output-1.png}
+	\caption{Average number of hydrogen bonds per molecule along $z$ at different temperatures.}
+	\label{fig:nhb}
+\end{figure}
+
+Figure \ref{fig:nhb} shows the average number of hydrogen bonds per molecule along $z$.
+In the bulk (slab center), each molecule forms about 3.4 hydrogen bonds at 280 K; higher temperatures reduce this number.
+
+\subsubsection{Orientational distributions and dangling hydrogens}
+
+\begin{figure}[htbp]
+\centering
+\begin{minipage}{0.4\linewidth}
+\centering
+\includegraphics[width=0.9\linewidth]{output-2.png}
+\caption{Dipole angle relative to the $z$-axis at different temperatures.}
+\label{fig:dipole}
+\end{minipage}
+\begin{minipage}{0.4\linewidth}
+\centering
+\includegraphics[width=0.9\linewidth]{output-4.png}
+\caption{Dangling O–H angles at 280 K.}
+\label{fig:dang_280K}
+\end{minipage}
+% 换行后继续插入
+\begin{minipage}{0.4\linewidth}
+\centering
+\includegraphics[width=0.9\linewidth]{output-5.png}
+\caption{Dangling O–H angles at 300 K.}
+\label{fig:dang_300K}
+\end{minipage}
+\begin{minipage}{0.4\linewidth}
+\centering
+\includegraphics[width=0.9\linewidth]{output-6.png}
+\caption{Dangling O–H angles at 320 K.}
+\label{fig:dang_320K}
+\end{minipage}
+\end{figure}
+
+Figures \ref{fig:dipole}–\ref{fig:dang_320K} show the average dipole angle and O–H angles for dangling and all hydrogens.
+The fraction of dangling hydrogens rises near the interface and with increasing temperature.
+Dipole and O–H orientations show pronounced interfacial alignment but remain statistically similar across temperatures.
+
+\subsubsection{Micro-structure analysis}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.3]{output-7.png}
+	\caption{Distribution of angles between molecules sharing a common hydrogen-bond acceptor at 300 K.}
+	\label{fig:micro_300K}
+\end{figure}
+
+Figure \ref{fig:micro_300K} shows the scatter plot of angles between molecules that hydrogen‑bond to the same molecule, using uniformly selected configurations at 300 K.
+In the bulk, a peak appears near $109.5^\circ$, while a weaker peak around $120^\circ$ emerges near the interface.
+
+\subsection{Discussion}
+
+At 280 K, the bulk hydrogen-bond count is about 3.4, indicating a well-connected network.
+As temperature rises to 300 K and 320 K, the average decreases to ~3.2 and ~3.1, respectively, reflecting thermal disruption of hydrogen bonds.
+
+Dipole orientations, dangling O–H angles, and dangling‑hydrogen fractions change markedly near the interface compared to the bulk.
+O–H bonds and molecular dipoles tend to point toward the vapor phase at all temperatures.
+However, these orientational profiles show little temperature dependence, suggesting thermal effects have limited influence on interfacial alignment.
+
+The angle distribution between hydrogen‑bonded molecules shows a strong peak near $109.5^\circ$ in the bulk, consistent with tetrahedral coordination.
+Near the interface, a secondary peak around $120^\circ$ appears, indicating equilateral‑triangle arrangements formed by hydrogen bonds.
+
+\section{Conclusion}
+
+This study used molecular dynamics simulations with the TIP4P/2005 model to investigate water structure at the air–water interface.
+We analyzed hydrogen-bond distributions, orientational profiles of O–H bonds and molecular dipoles, and local microstructure.
+Results show that hydrogen bonding decreases with temperature, while the fraction of dangling hydrogens increases near the interface.
+Orientational profiles remain largely temperature‑independent.
+Microstructure analysis reveals tetrahedral coordination in the bulk and equilateral‑triangle arrangements near the interface.
+These findings advance the microscopic understanding of interfacial water structure and its thermal response.
+
+\section{Team Contribution}
+
+\begin{itemize}
+	\item Jiarui HE : Hydrogen-bond analysis, O-H orientation and dangling hydrogen analysis, Micro-structure analysis.
+	\item Zhiyuan WANG: Dipole angle analysis, Simulation setup, Data processing scripts.
+\end{itemize}
+
+\printbibliography[title=References]
 

### 2025-12-07 UCUG1077/review/main.tex
add literature review of UCUG1077

% !TeX encoding = UTF-8
% !TeX program = xelatex
% !TeX spellcheck = en_US

\documentclass{template/cjc}

\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{siunitx}

\classsetup{
  % 配置里面不要出现空行
  title        = {自然语言处理模型的发展现状和未来展望},
  title*       = {The Development Status and Future Prospects of Natural Language Models},
  authors      = {
    author1 = {
      name         = {何家睿},
      name*        = {Jiarui HE},
      affiliations = {aff1},
      biography    = {男，2005年生，BEng(AI)，学生，主要研究领域为自然语言处理模型},
      % 英文作者介绍内容包括：出生年, 学位(或目前学历), 职称, 主要研究领域(与中文作者介绍中的研究方向一致).
      biography*   = {Undergraduate. His research interests include natural language processing},
      email        = {jhe218@connect.hkust-gz.edu.cn},
      phone-number = {13620853161},  % 第1作者手机号码(投稿时必须提供，以便紧急联系，发表时会删除)
    },
  },
  % 论文定稿后，作者署名、单位无特殊情况不能变更。若变更，须提交签章申请，
  % 国家名为中国可以不写，省会城市不写省的名称，其他国家必须写国家名。
  affiliations = {
    aff1 = {
      name  = {香港科技大学（广州）\ AI Thrust, 广州市 中国\ 511400},
      name* = {Hong Kong University of Science and Technology (Guangzhou), University, Guangzhou 511400, China},
    }
  },
  abstract     = {无. },
  abstract*    = {None},
  % 中文关键字与英文关键字对应且一致，应有5-7个关键词，不要用英文缩写
  keywords     = {综述，自然语言处理，大语言模型},
  keywords*    = {Survey, Natural Language Processing, Large Language Models},
  grants       = {},
  % clc           = {TP393},
  % doi           = {10.11897/SP.J.1016.2020.00001},  % 投稿时不提供DOI号
  % received-date = {2019-08-10},  % 收稿日期
  % revised-date  = {2019-10-19},  % 最终修改稿收到日期，投稿时不填写此项
  % publish-date  = {2020-03-16},  % 出版日期
  % page          = 512,
}

\newcommand\dif{\mathop{}\!\mathrm{d}}

% hyperref 总是在导言区的最后加载
\usepackage{hyperref}

\begin{document}

\maketitle

\section{引言}

自然语言处理（Natural Language Processing，NLP）\cite{jm3} 是研究计算机如何理解、生成和利用人类语言的一门交叉学科，横跨计算语言学、机器学习与人工智能。传统上，NLP 包含文本/语音的表示、句法与语义分析、信息抽取、机器翻译、问答与对话系统等任务。近年来，神经网络与大规模预训练语料的出现，为 NLP 带来了效果的质的飞跃，也促发了架构系统性变革。

本文梳理了主要模型与架构设计，并介绍用于扩展模型容量与效率的技术路线代表。同时，我们将讨论当前模型面临的幻觉现象。最后，在未来展望部分对研究与工程最有影响的路线。

\section{主要模型和架构发展}

\subsection{早期神经网络在NLP中的应用}

神经概率网络模型 \cite{bengio_neural_nodate} 使用多层神经网络学习并推理句子中出现的每个词的概率。具体而言，它处理的是，对于一个给定的上下文 $C$, 预测句子 $w_1, w_2, \dots w_T$ 中每个位置 $t$ 是词 $i$ 的概率 $P(w_t = i | C)$。此方法取得了较为优异的效果，但只能处理固定长度的上下文。

为了解决上下文长度的限制, 循环神经网络 (RNN) 被应用到自然语言处理中 \cite{mikolov_recurrent_2010} 。它天然利用了其 RNN 对序列数据的建模能力。然而，RNN 在处理长距离依赖关系时性能较差，这限制了其在复杂语言任务中的表现。

此后，Word2Seq \cite{mikolov_efficient_2013} 中提出了一种可以高效训练词向量的方法，通过跳字模型 (Skip-gram) 和连续词袋模型 (CBOW) 来捕捉词语之间的语义关系。这种方法极大地提升了词向量的质量，可以在大规模训练数据上表现良好且效率很高，并在多个 NLP 任务中取得了显著的效果。

\subsection{Transformer 架构}

Transformer \cite{vaswani_attention_2017} 引入了自注意力机制，允许模型在处理输入序列时动态地关注不同位置的信息，从而更好地捕捉长距离依赖关系。其架构由编码器和解码器组成，编码器负责将输入序列转换为隐藏表示，解码器则根据隐藏表示生成输出序列。与传统的模型相比，Transformer 具有更高的并行计算能力和更强的表达能力，并成为至今的大语言模型的基础架构。但其完全的注意力矩阵计算复杂度为 $O\left(n^2\right)$，对存储资源和计算资源要求较高。图片 \ref{fig:transformer} 展示了 Transformer 的基本结构。

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{transformer.png}
  \caption{Transformer 架构示意图 \cite{vaswani_attention_2017}。}
  \label{fig:transformer}
\end{figure}

\section{大语言模型的改进和拓展}

\subsection{稀疏注意力机制}

为了解决自注意力机制计算和存储复杂度过大的问题，研究人员提出了稀疏注意力机制。 Cluster-Former \cite{wang_cluster-former_2021} 使用滑动窗口来分割序列，并使用聚类方法聚合片段信息。交替进行分割和聚类能够既保留局部细节，又允许长距离信息整合。原生稀疏注意力 \cite{yuan_native_2025} 则通过动态分层稀疏策略，以及硬件对齐和特化的算法实现，显著加速了超长序列的处理。本方法还允许模型动态学习稀疏方式以适应不同任务。

\subsection{低秩适配器}

为获得针对特定任务的模型，研究人员往往需要对模型进行微调。然而，直接微调整个大模型会带来高昂的计算和存储成本。低秩适配器（Low-Rank Adapter, LoRA） \cite{hu_lora_2021} 是一种高效的微调方法，通过在预训练模型的权重矩阵上添加低秩矩阵来实现调整。具体而言，LoRA 训练两个低秩矩阵 $A\in\mathbb{R}^{d\times r}$，$B\times \mathbb{R}^{r\times k}$，然后将权重更新为 $W'=W+AB\in\mathbb{R}^{d\times k}$ 。其中 $r$ 远小于 $d$ 和 $k$。这种方法显著减少了需要更新的参数数量，从而降低了微调成本。利用了预训练模型的知识的同时，适应了特定任务的需求。

\subsection{量化技术}

为了解决现代模型参数量过大的问题，量化技术，即用较低精度的数据类型来压缩模型实际体积的技术，被广泛运用。

GPTQ \cite{frantar_gptq_2023} 使用了高效的后训练量化。它利用二阶信息，对预训练模型的权重进行量化，同时优化量化误差。使得一部分原本只能在大型服务器上运行的模型，可以在单个 GPU 上高效推理，且几乎无性能损失。Deepseek-V3 \cite{deepseek-ai_deepseek-v3_2025} 则在训练和部署中使用了混合精度量化技术，部分敏感操作保留较高精度，其余部分使用较低精度，大幅提高了训练和推理的效率。

\section{幻觉现象}

大模型在生成文本时，可能会出现幻觉现象，即生成与事实不符或完全虚构的信息，严重影响了模型的可靠性。

为解决这个问题，HalluLens \cite{bang_hallulens_2025} 提出了一个用于评估大语言模型生成文本中的幻觉现象的评分系统，帮助研究人员更好地理解和量化幻觉现象的严重程度。此外，哈尔滨工业大学和华为共著的综述 \cite{huang_survey_2025} 系统梳理了当前大语言模型幻觉的分类，成因，检测和缓解方法。

\section{未来展望}

NLP 模型的其中一个发展方向将会是提升模型的推理和训练效率，以更好地适应大规模数据和复杂任务的需求。同时，针对不同任务特化的模型设计也将成为未来的研究重点。

目前幻觉现象没有得到根本解决，需要进一步探索模型架构、训练数据和优化方法，以减少幻觉现象的发生，提高模型生成文本的准确性和可靠性。

\section{总结}

本文总结了自然语言处理模型的发展现状和未来展望。我们回顾了早期神经网络在 NLP 中的应用，介绍了 Transformer 架构及其改进方法，如低秩适配器，稀疏注意力机制和量化技术。可以发现 NLP 模型的发展经历从追求模型能力到提升模型效率的变化。

此外，我们讨论了大模型中常见的幻觉现象及其潜在解决方案。最后，我们展望了未来 NLP 领域的发展方向，强调了提升模型效率，针对性特化和减少幻觉现象的重要性。随着技术的不断进步，NLP 模型有望在更多实际应用中发挥更大的作用。

\bibliographystyle{template/cjc}
\bibliography{main}

\end{document}
